---
title: "Endurance_GS2021_PilotData"
author: "Anna Steel"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

library(tidyverse)
library(chron)
library(car)
library(lubridate)
library(lme4)

library(rethinking)

```



# *Green Sturgeon* #

### Read data
```{r read data, echo=FALSE}
endat = read.csv("rawdata/EnduranceGS2021.csv")
```

### Clean data
```{r clean, echo=FALSE}

endat$trialDate = as.Date(endat$trialDate, format="%m/%d/%y")
endat$hatchDate = as.Date(endat$hatchDate, format="%m/%d/%y")
endat$startTime.time = hm(endat$startTime)
endat$fatigueTimeSec = as.numeric(hms(endat$fatigueTime))
 

```

### Plot
```{r plot expt conditions, echo=FALSE}

## look at potential bias due to experimentally controlled variables ##

# size by treatment (is there bais?)
ggplot(data=endat[!is.na(endat$TLcm),],
       aes(x=factor(nomconc), y=TLcm, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

ggplot(data=endat[!is.na(endat$weightg),],
       aes(x=factor(nomconc), y=weightg, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

# run temp by treatment (is there bias?)
ggplot(data=endat[!is.na(endat$startTemp),],
       aes(x=factor(nomconc), y=startTemp, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

# temp change by treatment (is there bias?)
ggplot(data=endat[!is.na(endat$startTemp) & !is.na(endat$endTemp),],
       aes(x=factor(nomconc), y=(endTemp - startTemp), fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

# start time by treatment (is there bias?)
ggplot(data=endat,
       aes(x=factor(nomconc), y=(as.numeric(startTime.time))/3600, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + ylab("time of day (hrs)")+
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  
### nothing looks concerning. 
```
```{r data distns, echo=F}
hist(endat$fatigueTimeSec, breaks=25)
hist(log(endat$fatigueTimeSec), breaks=25)

```
```{r plot data, echo=F}
## look at results ##

# fatigue time by treatment
ggplot(data = endat[!is.na(endat$nomconc),], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))

# fatigue time by treatment, if swam > 1min
ggplot(data = endat[!is.na(endat$nomconc) & endat$fatigueTimeSec>1*60,], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))

# fatigue time by treatment, if swam > 3min #likely cuttoff for WS participation; here this removes 27 of 164 fish (16.5%)
ggplot(data = endat[!is.na(endat$nomconc) & endat$fatigueTimeSec>3*60,], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))

# fatigue time by treatment, if swam > 5min
ggplot(data = endat[!is.na(endat$nomconc) & endat$fatigueTimeSec>5*60,], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))


# fatigue by length, scatter plot, show those that swam the full trial
ggplot(data=endat[!is.na(endat$TLcm),],
       aes(x=TLcm, y=fatigueTimeSec, fill=factor(nomconc), group=factor(nomconc)))+
  geom_point(pch=21, size=3) + theme_bw() + 
  geom_point(data=endat[!is.na(endat$TLcm) & !is.na(endat$nomconc) & endat$fatigueTimeSec==7200,], pch=16, size=3) + scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue")) + geom_smooth(span=1.5, color="black", lwd=.4) + 
  facet_wrap(~nomconc)

# fatigue by mass, scatter plot
ggplot(data=endat[!is.na(endat$weightg) & !is.na(endat$nomconc),],
       aes(x=weightg, y=fatigueTimeSec, fill=factor(nomconc), group=factor(nomconc)))+
  geom_point(pch=21, size=3) + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue")) + geom_smooth(span=1.5, color="black", lwd=.4) + 
  facet_wrap(~nomconc)

# fatigue by temp, scatter plot
ggplot(data=endat[!is.na(endat$startTemp) & !is.na(endat$nomconc),],
       aes(x=startTemp, y=fatigueTimeSec, fill=factor(nomconc), group=factor(nomconc)))+
  geom_point(pch=21, size=3) + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue")) + geom_smooth(span=1.5, color="black", lwd=.4) + 
  facet_wrap(~nomconc)


```

### Stats Models
```{r stats}

moddat = endat[,c("fatigueTimeSec", "nomconc", "trialRound", 
                  "startTemp", "TLcm", "weightg")]
 moddat = moddat[!is.na(moddat$nomconc),]
moddat$lnsec = log(moddat$fatigueTimeSec)
moddat$lnConc = log(moddat$nomconc+1)
moddat$lnConcC = as.numeric(scale(moddat$lnConc, scale=F))
moddat$startTempC = as.numeric(scale(moddat$startTemp, scale=F))
moddat$TLcmC = as.numeric(scale(moddat$TLcm, scale=F))
moddat$weightgC = as.numeric(scale(moddat$weightg, scale=F))
 # don't have actual concentraqtions yet, so add measured conc when we get them

moddat3min = moddat[moddat$fatigueTimeSec>(3*60),]
moddat3min$lnConcC = as.numeric(scale(moddat3min$lnConc, scale=F))
moddat3min$startTempC = as.numeric(scale(moddat3min$startTemp, scale=F))
moddat3min$TLcmC = as.numeric(scale(moddat3min$TLcm, scale=F))
moddat3min$weightgC = as.numeric(scale(moddat3min$weightg, scale=F))


gs.end.nlt = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC + bt*startTemp,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
        bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low, esp for a and bt


gs.end.nlt3 = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC + bt*startTemp,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
        bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat3min, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low, esp for a and bt
    

gs.end.l = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bl*TLcmC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bl ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
  # trace plots look good
  # neff/Rhat look good

    

gs.end.n = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
 # trace plots look good
 # neff/Rhat good
    

gs.end.t = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bt*startTemp,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low and Rhat high (1.04)
    

gs.end.nl = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
  # trace plots look good
  # neff/Rhat good
    

gs.end.nl3 = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat3min, iter = 2000, warmup = 500, chains = 4)
 # trace plots look good
  # neff/Rhat good
    

gs.end.lt = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound]  + bl*TLcmC + bt*startTemp,
       a_rnd[trialRound] ~ dnorm(a,a_sig), 
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
       bl ~ dnorm(0,10),
       bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low and Rhat high (1.04)

gs.end.anlt = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a + bn*lnConcC + bl*TLcmC + bt*startTemp,
       a ~ dnorm(0,10),
       bn ~ dnorm(0,10),
       bl ~ dnorm(0,10),
       bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddat, iter = 2000, warmup = 500, chains = 4)
  # trace plots look good
  # neff/Rhat good

   plot(compare(gs.end.nlt, gs.end.l, gs.end.n, gs.end.t, gs.end.nl, gs.end.lt, gs.end.anlt))
   plot(compare(gs.end.nlt3, gs.end.nl3))
```
## Models with a random effect for trial round and an effect for temperature don't mix very well. Likely because the temperature is the same for all fish in a round, and thus the effect of each is hard to differentiate. But the model that includes temp and not a random effect for round doesn't perform as well as the one with the random effect, according to WAIC. All models that include nominal concentration perform worse than those that do not include it - in other words, nomconc is not a useful predictor, and both water temperature and fish length are better predictors, when the clustering by round is accounted for. 
## I will select nl (or nl3) as the model to intepret, so I can discuss the small effect of nomconc in relation to size, and can highlight the effect of temperature through the grouping variable. I'll ask Zack if the trace plots are good enough to use temp as a predictor, but I expect not. 


```{r predict from model nl and nl3}

# pull posterior from model:
set.seed(42)
post = extract.samples(gs.end.nl)
post3 = extract.samples(gs.end.nl3)

# set up dataframe to plot posterior predictions at the average fish length
preddat = data.frame(expand_grid(conc=seq(0, 1000, 2), 
              TLcm = mean(moddat3min$TLcm), 
              trialRound = 1))
 preddat$TLcmC = preddat$TLcm -  mean(moddat3min$TLcm)
 preddat$lnConc = log(preddat$conc+1)
 preddat$lnConcC= preddat$lnConc - mean(moddat3min$lnConc) 
 

# replace individual fish estimates with global estimate; this should predict to the average individual in a population...so since I want to get at the population level response this seems more appropriate.
a_global = matrix(post$a,6000,19)

# use link to predict to mean only
link.gs.end.nl <- link(gs.end.nl, n=1000, data= preddat, 
                         replace = list(a_rnd = a_global) )
link.gs.end.nl3 <- link(gs.end.nl3, n=1000, data= preddat, 
                         replace = list(a_rnd = a_global) )

preddat.df <- preddat
  #data.frame(sapply(preddat,c)) # thanks stack overflow! https://stackoverflow.com/questions/4227223/convert-a-list-to-a-data-frame

preddat.df$link_mu_mn <- apply(link.gs.end.nl3, 2, mean) 
preddat.df$link_PI05 = apply(link.gs.end.nl3, 2, PI, .95)[1,] 
preddat.df$link_PI95 = apply(link.gs.end.nl3, 2, PI, .95)[2,] 


gs.end.transf3 = ggplot() + 
  geom_point(data=moddat3min,
             aes(x=(lnConcC),                          
                 y=lnsec)) + 
  geom_ribbon(data = preddat.df, aes(x=(lnConcC), 
              ymin=link_PI05, ymax=link_PI95), 
              alpha=.4, col="grey70")+
  geom_line(data = preddat.df, aes(x=(lnConcC), y=link_mu_mn), lwd=.2)+
    ylab("ln(Seconds to Fatigue)") + #ylim(c(3.5, 8.5)) + 
    scale_x_continuous(name="ln(Nominal Fipronil Concentration (ug/L))") + 
    theme_bw()
gs.end.transf


gs.end.orig3 = ggplot() + 
  geom_point(data=moddat3min,
             aes(x=(nomconc),                          
                 y=fatigueTimeSec)) + 
  geom_ribbon(data = preddat.df, aes(x=(conc), 
              ymin=exp(link_PI05), ymax=exp(link_PI95)), 
              alpha=.4, col="grey70")+
  geom_line(data = preddat.df, aes(x=(conc), y=exp(link_mu_mn)), lwd=.2)+
  ylab("Time to Fatigue (s)") + 
  scale_x_continuous(name="Fipronil Concentration (ug/L)") +
  theme_bw()

gs.end.transf3
gs.end.orig3

tiff("figures/GS_endurance_Fip2021_modelpredictions.tiff", width=165, height=100, units="mm", res=300)
gs.end.orig3
dev.off()
```

```{r contrasts from model nl3}
set.seed(1983) 
postdist = extract.samples(gs.end.nl3)  

# calculate differences between control and treatment at each time point for each species (20 contrasts)
GS0 = postdist$a +
  postdist$bn*unique(subset(moddat3min, nomconc==0)$lnConcC) +
  postdist$bl*mean(moddat3min$TLcmC)
GS1 = postdist$a + 
  postdist$bn*unique(subset(moddat3min, nomconc==1)$lnConcC) +
  postdist$bl*mean(moddat3min$TLcmC)
GS10 = postdist$a + 
  postdist$bn*unique(subset(moddat3min, nomconc==10)$lnConcC) +
  postdist$bl*mean(moddat3min$TLcmC)
GS100 = postdist$a + 
  postdist$bn*unique(subset(moddat3min, nomconc==100)$lnConcC) +
  postdist$bl*mean(moddat3min$TLcmC)
GS500 = postdist$a +
  postdist$bn*unique(subset(moddat3min, nomconc==500)$lnConcC) +
  postdist$bl*mean(moddat3min$TLcmC)
GS1000 = postdist$a + 
  postdist$bn*unique(subset(moddat3min, nomconc==1000)$lnConcC) +
  postdist$bl*mean(moddat3min$TLcmC)

CI95func = function(x) {
  line = c(CI95L=quantile(x,.025), 
                  Median=median(x), 
                  Mean=mean(x), 
                  CI96U=quantile(x,.0975)) 
  print(line)}

CI95func(GS0)
CI95func(GS1)
CI95func(GS10)
CI95func(GS100)
CI95func(GS500)
CI95func(GS1000)

 cont.GS0.1 = (sum(GS0<GS1) / length(GS0)) 
 cont.GS0.1 #46.7% prob that 1 has longer swim time than 0

 cont.GS0.10 = (sum(GS0<GS10) / length(GS0)) 
 cont.GS0.10 #46.7% prob that 10 has longer swim time than 0
 
 cont.GS0.100 = (sum(GS0<GS100) / length(GS0)) 
 cont.GS0.100 #46.7% prob that 100 has longer swim time than 0
 
 cont.GS0.500 = (sum(GS0<GS500) / length(GS0)) 
 cont.GS0.500 #46.7% prob that 500 has longer swim time than 0
 
 cont.GS0.1000 = (sum(GS0<GS1000) / length(GS0)) 
 cont.GS0.1000 #46.7% prob that 1000 has longer swim time than 0
 
# they're all identical? To the 7th decimal place? Is that right? Yes. The estimate for bn is 0 (-0.04 to 0.02). Amazing. 
```





# *White Sturgeon* #



### Read data
```{r ws read data, echo=FALSE}
endatws = read.csv("rawdata/EnduranceWS2021.csv")
```

### Clean data
```{r ws clean, echo=FALSE}

endatws$trialDate = as.Date(endatws$trialDate, format="%m/%d/%y")
endatws$hatchDate = as.Date(endatws$hatchDate, format="%m/%d/%y")
endatws$startTime.time = hm(endatws$startTime)
endatws$fatigueTimeSec = as.numeric(hms(endatws$fatigueTime))
 

```

### Plot
```{r ws plot expt conditions, echo=FALSE}

## look at potential bias due to experimentally controlled variables ##

# size by treatment (is there bais?)
ggplot(data=endatws[!is.na(endatws$TLcm),],
       aes(x=factor(nomconc), y=TLcm, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

ggplot(data=endatws[!is.na(endatws$weightg),],
       aes(x=factor(nomconc), y=weightg, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

# run temp by treatment (is there bias?)
ggplot(data=endatws[!is.na(endatws$startTemp),],
       aes(x=factor(nomconc), y=startTemp, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

# temp change by treatment (is there bias?)
ggplot(data=endatws[!is.na(endatws$startTemp) & !is.na(endatws$endTemp),],
       aes(x=factor(nomconc), y=(endTemp - startTemp), fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  

# start time by treatment (is there bias?)
ggplot(data=endatws,
       aes(x=factor(nomconc), y=(as.numeric(startTime.time))/3600, fill=factor(nomconc), group=factor(nomconc)))+
  geom_boxplot() + theme_bw() + ylab("time of day (hrs)")+
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))  


# look at those that refused to swim
ggplot(data = endatws, aes(x=fatigueTimeSec, group=Refused, fill=Refused)) + geom_histogram(alpha=0.4, position="identity") + xlim(c(0,500)) + theme_bw()

ggplot(data = endatws[endatws$fatigueTimeSec>3*60 & endatws$weightg<3,], aes(x=fatigueTimeSec, group=Refused, fill=Refused)) + geom_histogram(alpha=0.4) + facet_wrap(~Refused, scales="free") 
 # the 'refused to swim' metric was valuable even after filtering by time > 3min. Bummer we don't have it for the GS. talk to Vanessa again.



### nothing looks concerning. Perhaps pink was swam at colder temps
```
```{r ws data distns, echo=F}
hist(endatws$fatigueTimeSec, breaks=25)
hist(log(endatws$fatigueTimeSec), breaks=25)

# issues with fish swimming to end of trial
```
```{r ws plot data, echo=F}
## look at results ##

# fatigue time by treatment
ggplot(data = endatws[!is.na(endatws$nomconc),], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))

# fatigue time by treatment, if swam > 1min
ggplot(data = endatws[!is.na(endatws$nomconc) & endatws$fatigueTimeSec>1*60,], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))

# fatigue time by treatment, if swam > 3min
ggplot(data = endatws[!is.na(endatws$TLcm) & endatws$fatigueTimeSec>3*60 ,], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))

# fatigue time by treatment, if swam > 5min
ggplot(data = endatws[!is.na(endatws$nomconc) & endatws$fatigueTimeSec>5*60,], 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot() + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))


# fatigue by length, scatter plot. Highlight those that swam the whole trial
ggplot(data=endatws[!is.na(endatws$TLcm) & endatws$fatigueTimeSec>3*60 & !is.na(endatws$nomconc),], ## the shortest swim time for fish classified as participants was 3:07, while the longest time for fish classifies as non-participants was 4:53. Selecting a cut-off of 3 minutes
       aes(x=TLcm, y=fatigueTimeSec, fill=factor(nomconc), group=factor(nomconc)))+
  geom_point(pch=21, size=3) + 
  geom_point(data=endatws[!is.na(endatws$TLcm) & endatws$fatigueTimeSec==7200 & !is.na(endatws$nomconc),], pch=16, size=3) + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue")) + geom_smooth(span=1.5, color="black", lwd=.4) + 
  facet_wrap(~nomconc)


# fatigue by mass, scatter plot. Highlight those that swam the whole trial
ggplot(data=endatws[!is.na(endatws$weightg) & endatws$fatigueTimeSec>3*60 & !is.na(endatws$nomconc),],
       aes(x=weightg, y=fatigueTimeSec, fill=factor(nomconc), group=factor(nomconc)))+
  geom_point(pch=21, size=3) + 
  geom_point(data=endatws[!is.na(endatws$weightg) & endatws$fatigueTimeSec==7200 & !is.na(endatws$nomconc),], pch=16, size=3) + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue")) + geom_smooth(span=1.5, color="black", lwd=.4) + 
  facet_wrap(~nomconc)


# fatigue relative to weight-length relationship
ggplot(data=endatws[!is.na(endatws$weightg) &!is.na(endatws$TLcm) & endatws$fatigueTimeSec>3*60 & !is.na(endatws$nomconc),],
       aes(y=weightg, x=TLcm, fill=fatigueTimeSec, group=fatigueTimeSec))+
  geom_point(pch=21, size=3) + 
  geom_point(data=endatws[!is.na(endatws$weightg) &!is.na(endatws$TLcm) & endatws$fatigueTimeSec==7200 & !is.na(endatws$nomconc),], pch=16, size=3, color="red") + theme_bw() + 
 facet_wrap(~nomconc)


# fatigue by temp, scatter plot. Highlight those that swam the whole trial
ggplot(data=endatws[!is.na(endatws$startTemp) & endatws$fatigueTimeSec>3*60 & !is.na(endatws$nomconc),],
       aes(x=startTemp, y=fatigueTimeSec, fill=factor(nomconc), group=factor(nomconc)))+
  geom_point(pch=21, size=3) + geom_point(data=endatws[!is.na(endatws$weightg) &!is.na(endatws$TLcm) & endatws$fatigueTimeSec==7200 & !is.na(endatws$nomconc),], pch=16, size=3, color="red") + theme_bw() + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue")) + geom_smooth(span=1.5, color="black", lwd=.4) + 
  facet_wrap(~nomconc)


# filter out those that didn't participate, and that were >3g weightg (see less trend by size at this threshold)
subdat = endatws[!is.na(endatws$TLcm)  & !is.na(endatws$nomconc) & endatws$weightg<3 & endatws$Refused=="n",]# endatws$fatigueTimeSec>5*60,]#& endatws$TLcm<9.5,]
# TLcm<9.5 removes only 5 of 16 that swam the whole time. 
# weightg<3 removed of 9 of 16 that swam the whole time; rest distributed somewhat evenly across treatments (3 control, 1 green, 1 yellow, 1 red, 1 pink).
# think more on how to deal with these; if I need a cox model. =/
ggplot(data = subdat, 
       aes(x=factor(nomconc), y=fatigueTimeSec, 
           group=factor(nomconc), fill=factor(nomconc))) + 
  geom_boxplot(outlier.size=0.5) + theme_bw() + 
  geom_point(pch=1, position="jitter") + 
  scale_fill_manual(values=c("white","seagreen3","gold","firebrick2","pink","skyblue"))


```

### Stats Models
```{r ws stats}

moddatws = endatws[,c("fatigueTimeSec", "nomconc", "trialRound", 
                  "startTemp", "TLcm", "weightg","Refused")]
 moddatws = moddatws[!is.na(moddatws$nomconc),]
 moddatws = moddatws[!is.na(moddatws$TLcm),]

moddatws$lnsec = log(moddatws$fatigueTimeSec)
moddatws$lnConc = log(moddatws$nomconc+1)
moddatws$lnConcC = as.numeric(scale(moddatws$lnConc, scale=F))
moddatws$startTempC = as.numeric(scale(moddatws$startTemp, scale=F))
moddatws$TLcmC = as.numeric(scale(moddatws$TLcm, scale=F))
moddatws$weightgC = as.numeric(scale(moddatws$weightg, scale=F)) 
  
moddatwspart = moddatws[moddatws$Refused=="n",]
moddatwspart3g = moddatws[moddatws$Refused=="n" & moddatws$weightg<3,]

moddatwspart3g$lnsec = log(moddatwspart3g$fatigueTimeSec)
moddatwspart3g$lnConc = log(moddatwspart3g$nomconc+1)
moddatwspart3g$lnConcC = as.numeric(scale(moddatwspart3g$lnConc, scale=F))
moddatwspart3g$startTempC = as.numeric(scale(moddatwspart3g$startTemp, scale=F))
moddatwspart3g$TLcmC = as.numeric(scale(moddatwspart3g$TLcm, scale=F))
moddatwspart3g$weightgC = as.numeric(scale(moddatwspart3g$weightg, scale=F))
 # don't have actual concentraqtions yet, so add measured conc when we get them

ws.end.nlt.p = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC + bt*startTemp,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
        bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low, esp for a and bt
    

ws.end.nlt.p3 = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC + bt*startTemp,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
        bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart3g, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low, esp for a and bt
    

ws.end.l.p = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bl*TLcmC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bl ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart, iter = 2000, warmup = 500, chains = 4)
  # trace plots look good
  # neff/Rhat look good

    

ws.end.n.p = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart, iter = 2000, warmup = 500, chains = 4)
 # trace plots look good
 # neff/Rhat good
    


ws.end.n.p3 = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart3g, iter = 2000, warmup = 500, chains = 4)
 # trace plots look good
 # neff/Rhat good
    

ws.end.t.p = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bt*startTemp,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bt ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty wiggly for a_rnd and bt
  # neff low and Rhat high (1.04)
    

ws.end.nl.p = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart, iter = 2000, warmup = 500, chains = 4)
  # trace plots look pretty good
  # neff /Rhat good
    

ws.end.nl.p3 = map2stan(
  alist(
    lnsec ~ dnorm(mu, sigma),
    mu  <- a_rnd[trialRound] + bn*lnConcC + bl*TLcmC,
        a_rnd[trialRound] ~ dnorm(a,a_sig),
           a ~ dnorm(0,10),
           a_sig ~ dcauchy(0,10),
        bn ~ dnorm(0,10),
        bl ~ dnorm(0,10),
    sigma ~ dcauchy(0,10)
    ) ,
  data = moddatwspart3g, iter = 2000, warmup = 500, chains = 4)
 # trace plots look pretty good
  # neff /Rhat good
    

   plot(compare(ws.end.nlt.p, ws.end.l.p, ws.end.n.p, ws.end.t.p, ws.end.nl.p))
   plot(compare(ws.end.nlt.p3, ws.end.nl.p3, ws.end.n.p3))
```
## Models with a random effect for trial round and an effect for temperature don't mix very well. Likely because the temperature is the same for all fish in a round, and thus the effect of each is hard to differentiate. But the GS model that includes temp and not a random effect for round doesn't perform as well as the one with the random effect, according to WAIC. All models that include nominal concentration perform worse than those that do not include it - in other words, nomconc is not a useful predictor, and both water temperature and fish length are better predictors, when the clustering by round is accounted for. For WS the length predictor is the best one, which makes sense because the raw data plots show a clear trend by size. This trend for model performance holds when we remove all fish over 3g, but the size of the WAIC difference is smaller (14.6 vs 8.5)
## I will select nl as the model to intepret, so I can discuss the small effect of nomconc in relation to size, and can highlight the effect of temperature through the grouping variable. For WS I'll drop all fish > 3. For both datasets I'll drop either the non-participants (WS) or the fish which swam less than 3 min (GS). 


```{r ws predict from model nl}

# pull posterior from model:
set.seed(42)
post = extract.samples(ws.end.nl.p3)

# set up dataframe to plot posterior predictions at the average fish length
preddat = data.frame(expand_grid(conc=seq(0, 1000, 2), 
              TLcm = mean(moddatwspart3g$TLcm), 
              trialRound = 1))
 preddat$TLcmC = preddat$TLcm -  mean(moddatwspart3g$TLcm)
 preddat$lnConc = log(preddat$conc+1)
 preddat$lnConcC= preddat$lnConc - mean(moddatwspart3g$lnConc) 
 

# replace individual fish estimates with global estimate; this should predict to the average individual in a population...so since I want to get at the population level response this seems more appropriate.
a_global = matrix(post$a,6000,19)

# use link to predict to mean only
link.ws.end.nl.p3 <- link(ws.end.nl.p3, n=1000, data= preddat, 
                         replace = list(a_rnd = a_global) )

preddat.df <- preddat
  #data.frame(sapply(preddat,c)) # thanks stack overflow! https://stackoverflow.com/questions/4227223/convert-a-list-to-a-data-frame

preddat.df$link_mu_mn <- apply(link.ws.end.nl.p3, 2, mean) 
preddat.df$link_PI05 = apply(link.ws.end.nl.p3, 2, PI, .95)[1,] 
preddat.df$link_PI95 = apply(link.ws.end.nl.p3, 2, PI, .95)[2,] 


ws.end.transf3 = ggplot() + 
  geom_point(data=moddatwspart3g,
             aes(x=(lnConcC),                          
                 y=lnsec)) + 
  geom_ribbon(data = preddat.df, aes(x=(lnConcC), 
              ymin=link_PI05, ymax=link_PI95), 
              alpha=.4, col="grey70")+
  geom_line(data = preddat.df, aes(x=(lnConcC), y=link_mu_mn), lwd=.2)+
    ylab("ln(Seconds to Fatigue)") + 
    scale_x_continuous(name="ln(Nominal Fipronil Concentration (ug/L))") + ggtitle("White Sturgeon")+
    theme_bw()
ws.end.transf3


ws.end.orig3 = ggplot() + 
  geom_point(data=moddat,
             aes(x=(nomconc),                          
                 y=fatigueTimeSec)) + 
  geom_ribbon(data = preddat.df, aes(x=(conc), 
              ymin=exp(link_PI05), ymax=exp(link_PI95)), 
              alpha=.4, col="grey70")+
  geom_line(data = preddat.df, aes(x=(conc), y=exp(link_mu_mn)), lwd=.2)+
  ylab("Time to Fatigue (s)") + ggtitle("White Sturgeon")+
  scale_x_continuous(name="Fipronil Concentration (ug/L)") +
  theme_bw()

ws.end.transf3
ws.end.orig3

tiff("figures/WS_endurance_Fip2021_modelpredictions.tiff", width=165, height=100, units="mm", res=300)
ws.end.orig3
dev.off()
```

```{r ws contrasts from model nl.p3}
set.seed(1983) 
postdist = extract.samples(ws.end.nl.p3)  

# calculate differences between control and treatment
WS0 = postdist$a +
  postdist$bn*unique(subset(moddatwspart3g, nomconc==0)$lnConcC) +
  postdist$bl*mean(moddatwspart3g$TLcmC)
WS1 = postdist$a + 
  postdist$bn*unique(subset(moddatwspart3g, nomconc==1)$lnConcC) +
  postdist$bl*mean(moddatwspart3g$TLcmC)
WS10 = postdist$a + 
  postdist$bn*unique(subset(moddatwspart3g, nomconc==10)$lnConcC) +
  postdist$bl*mean(moddatwspart3g$TLcmC)
WS100 = postdist$a + 
  postdist$bn*unique(subset(moddatwspart3g, nomconc==100)$lnConcC) +
  postdist$bl*mean(moddatwspart3g$TLcmC)
WS500 = postdist$a +
  postdist$bn*unique(subset(moddatwspart3g, nomconc==500)$lnConcC) +
  postdist$bl*mean(moddatwspart3g$TLcmC)
WS1000 = postdist$a + 
  postdist$bn*unique(subset(moddatwspart3g, nomconc==1000)$lnConcC) +
  postdist$bl*mean(moddatwspart3g$TLcmC)

CI95func = function(x) {
  line = c(CI95L=quantile(x,.025), 
                  Median=median(x), 
                  Mean=mean(x), 
                  CI96U=quantile(x,.0975)) 
  print(line)}

CI95func(WS0)
CI95func(WS1)
CI95func(WS10)
CI95func(WS100)
CI95func(WS500)
CI95func(WS1000)

 cont.WS0.1 = (sum(WS0<WS1) / length(WS0)) 
 cont.WS0.1 #38.5% prob that 1 has longer swim time than 0 (more likely that 0 is longer than 1)

 cont.WS0.10 = (sum(WS0<WS10) / length(WS0)) 
 cont.WS0.10 #38.5% prob that 10 has longer swim time than 0
 
 cont.WS0.100 = (sum(WS0<WS100) / length(WS0)) 
 cont.WS0.100 #38.5% prob that 100 has longer swim time than 0
 
 cont.WS0.500 = (sum(WS0<WS500) / length(WS0)) 
 cont.WS0.500 #38.5% prob that 500 has longer swim time than 0
 
 cont.WS0.1000 = (sum(WS0<WS1000) / length(WS0)) 
 cont.WS0.1000 #38.5% prob that 1000 has longer swim time than 0
 
# they're all identical again? To the 7th decimal place? Is that right? Yes. The estimate for WS bn is -0.02 (-0.10 to 0.05). Hm. 
```
