---
title: "Exposure_Analysis2 - Exploratory Analysis"
author: "Anna Steel"
date: "9/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readtext) # need this because the ethovision output .txt files have unusual encoding as UTF-16
library(lme4)
#library(rethinking)
library(chron)
library(rprojroot) # only used for find_rstudio_root_file() to set project wd as root

knitr::opts_knit$set(root.dir = find_rstudio_root_file()) # sets root directory to match project directory, not rmd file location
```

```{r utility functions, include=FALSE}
# calculate hypotenuse of triangle created by two xy locations

distmov = function(x1,x2,y1,y2) { dm = sqrt((x1-x2)^2 + (y1-y2)^2); return(dm)}

# calculate number steps between detections; use summarized dataset (5 pos/sec)
nstep = function(t2,t1, interv=0.2) {
  if (t2-t1 < 0) stop('time steps backwards?')
  nstep <- ( (t2-t1) / interv)
  return(nstep)
  }


circ.mean.na = function(x) {
  x2 = x[!is.na(x)]
  sinr <- sum(sin(x2))
  cosr <- sum(cos(x2))
  circmean <- atan2(sinr, cosr)
  return(circmean)
}

circ.disp.na = function(x) {
  x2 = x[!is.na(x)]
    n <- length(x2)
    c <- sum(cos(x2))
    s <- sum(sin(x2))
    r <- sqrt(c^2 + s^2)
    rbar <- r/n
    var <- 1 - rbar
    data.frame(n, r, rbar, var)
}

```


## Read in Cleaned Data ("Exposure_Analysis1.Rmd")
```{r read in clean data}
DataSum2496 = read.csv("outputData/Exposure_Outputdata/Bifenthrin_2020_Cleaned_FullData.csv")
```


## Exploratory Plots for each metric (Total distance travelled, Mean velocity, Meander and Turn angle, Use of center zone (% time), Time Active, Full Rotations vs distance traveled) 
  
  
### Distance  
  
```{r distance data, echo=F}

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum96.dist = DataSum2496 %>%
  filter(ExposureHrs==96) %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum2496.dist = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()


```

```{r distance plots}
## with 96
totfishdist96_hist = ggplot(DataSum96.dist, aes(x=TotalfishDist_m) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(Treatment~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ 
                     theme_bw()

totfishdist96 = ggplot(DataSum96.dist, aes(fill=factor(Treatment), y=TotalfishDist_m, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~Spp, labeller = labeller(
                        Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                        scales="free") +
                      ylab("Total Trial Distance (m)") + 
                      xlab("Exposure Hours") +
                      scale_fill_viridis_d(name="Nominal Fpironil\nConcentration (ug/L)") + 
                      theme_bw()

totfishdist96


totfishdist_hist = ggplot(DataSum2496.dist, aes(x=TotalfishDist_m) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(Treatment~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ #scales="free") +
                     theme_bw()

totfishdist = ggplot(DataSum2496.dist, aes(fill=factor(Treatment), y=TotalfishDist_m, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~Spp, labeller = labeller(
                        Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),#)+
                        scales="free") +
                      ylab("Total Trial Distance (m)") + 
                      xlab("Exposure Hours") +#("Bifenthrin Nominal Conc.") + 
                      scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()

totfishdist

    totfishdist2496_Control = ggplot(DataSum2496.dist[DataSum2496.dist$Treatment==0,],
                                    aes(y=TotalfishDist_m, 
                                   x=factor(ExposureHrs),
                                   fill=Spp) ) + 
                          geom_boxplot(outlier.size = .75) + 
                          facet_wrap(~Spp, labeller = labeller(
                            Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
                          ylab("Total Trial Distance (m)") + 
                          xlab("Exposure Hours") +
                          scale_fill_manual(values=c("palegreen3","grey70"))+
                          theme_bw()
    
    totfishdist2496_Control
    
tiff("figures/Exposure_OutputFigs/TotalDistance_BifControl.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
totfishdist2496_Control
dev.off()
```

```{r visualizing as distributions of percent change with 96}

DataSum96.dist.cont = DataSum96.dist[DataSum96.dist$Treatment==0, c("Spp","ExposureHrs","Replicate","TotalfishDist_m")]
   DataSum96.dist.cont = rename(DataSum96.dist.cont,
                                 ControlTotaldist = TotalfishDist_m)
   
DataSum96.dist.treat = DataSum96.dist[DataSum96.dist$Treatment!=0, c("Spp","ExposureHrs","Replicate","Treatment","TotalfishDist_m")]

DataSum96.dist.pseudowide = merge(DataSum96.dist.treat, DataSum96.dist.cont, all.x=T)

dist.dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg96 = DataSum96.dist.pseudowide %>%
  group_by(Spp, Treatment, Replicate) %>%
  summarize(PercChg = dist.dist.func(a=ControlTotaldist, b=TotalfishDist_m)) %>%
           ungroup() %>% data.frame()

  PercChgGSlm = lm(PercChg ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgGSaov = aov(PercChgGSlm)
    summary(PercChgGSaov)
      TukeyHSD(PercChgGSaov)
       # nothing is significantly different
     
    PercChgWSlm = lm(PercChg ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgWSaov = aov(PercChgWSlm)
    summary(PercChgWSaov)
      TukeyHSD(PercChgWSaov)
       # difference between 2000 and 5:500 are significant @ p<0.02; nothing else
  
# are the boxes different from zero?      
onesamp.ttest <- PercChg96 %>%
  group_by(Spp, Treatment) %>%
  t_test(PercChg~1) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance() %>%
  data.frame()
onesamp.ttest
        

DistnChg96.dist = ggplot(PercChg96, 
                         aes(y=PercChg, x=factor(Treatment), fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="black")+
                       geom_boxplot(outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")) )+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="red")+
                       ylab("Change in Swimming Distance (m)") + ylim(c(-1,1)) +
                       xlab("Bifenthrin Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChg96.dist

tiff("/Users/Anna/Documents/ResearchGit/SturgContam/figures/Exposure_OutputFigs/TrialDistance_Bif96_Perchg.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
DistnChg96.dist
dev.off()

```

```{r other ways of visualizing distance}
## these were written prior to deciding how to visualize and plot change from control
#(which was updated Dec 2021)

 # look at the CHANGE between mean distance of control (mean for treatment-exposurehrs) and target conc (each individual)
 
MeanDist0 = DataSum2496.dist %>%
  subset(Treatment==0) %>%
  group_by(Spp, ExposureHrs) %>%
  summarize(mean0_dist = mean(TotalfishDist_m)) %>%
  ungroup %>% data.frame
DataSumDiff.dist = merge(DataSum2496.dist, MeanDist0, all.x=T)
DataSumDiff.dist$DistDiff = DataSumDiff.dist$TotalfishDist_m - DataSumDiff.dist$mean0_dist


  cntrlfishdist = ggplot(DataSumDiff.dist, 
                         aes(y=DistDiff, x=factor(Treatment),fill=factor(Treatment) ) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                       geom_boxplot(outlier.size = .75) + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hours exposed","96"="96 hours exposed")))+
                       ylab("Change in Swimming Distance (m)\n treatment vs control") + 
                       xlab("Bifenthirin Nominal Conc") +
                       scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                       theme_bw()
                          
  cntrlfishdist

  
  
# look at the change between 24 and 96 hours for each replicated individual
 
DataSum2496.dist$ExposureHrsChr = paste0("ExpHr",DataSum2496.dist$ExposureHrs)
DataSum2496.dist$lnCalcConc = log(DataSum2496.dist$calcConc+1)

DataSumChg.dist = DataSum2496.dist %>%
  pivot_wider(id_cols = c(RepID, Treatment, Spp, Replicate, calcConc, lnCalcConc), 
              names_from = ExposureHrs, names_prefix="TotDistAt", 
              values_from = TotalfishDist_m) %>%
  mutate(chngdist = TotDistAt96 - TotDistAt24) %>%
  data.frame



  chngfishdist.box = ggplot(DataSumChg.dist, 
                           aes(y=chngdist/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Distance\nfrom 24 to 96 hrs of exposure (m)") + 
                    xlab("Bifenthirin Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                    theme_bw()
  
  chngfishdist.box
  
  
  chngfishdist.py = ggplot(DataSumChg.dist, 
                           aes(y=chngdist/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Distance\nfrom 24 to 96 hrs of exposure (m)") + 
                  xlab("log(Bifenthirin Concentration (ng/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishdist.py
  
  
# do individuals consistently respond in the same way? Should I add a multilevel term for intercept or slope. Or both?
  
ggplot(DataSum2496.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=RepID)) + geom_point() + geom_line() + facet_grid(Spp~Treatment, scales="free") + theme(legend.position="none")
# looks like there is often a trend, but not always. I think a random slope between the two time points would be really helpful. 

ggplot(DataSum2496.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=Spp)) + geom_point() + geom_line() + facet_grid(Treatment~Replicate, scales="free") + theme_bw() + theme(legend.position="none")

```

### modelling for distance is in ExposureAnalysis3.rmd





### Velocity 
```{r velocity data, echo=F}

## Summarize movement velocity
 
DataSum2496.vel = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  summarize(MnVel = mean(MnVel, na.rm=T), npos = n()) %>%
  ungroup()  %>%
  data.frame()
```

```{r velocity plots}

MoveVel.plot = ggplot(DataSum2496.vel, 
                           aes(fill=factor(Treatment), y=MnVel, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Mean movement velocity (mm/s)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

MoveVel.plot
```

```{r other ways of visualizing velocity}

 # look at the CHANGE between mean vel of control (mean for treatment-exposurehrs) and target conc (each individual)
 
MeanVel0 = DataSum2496.vel %>%
  subset(Treatment==0) %>%
  group_by(Spp, ExposureHrs) %>%
  summarize(mean0_Vel = mean(MnVel)) %>%
  ungroup %>% data.frame

DataSumDiff.Vel = merge(DataSum2496.vel, MeanVel0, all.x=T)

DataSumDiff.Vel$VelDiff = DataSumDiff.Vel$MnVel - DataSumDiff.Vel$mean0_Vel


  cntrlfishVel = ggplot(DataSumDiff.Vel, 
                         aes(y=VelDiff/10, x=factor(Treatment),fill=factor(Treatment) ) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                       geom_boxplot(outlier.size = .75) + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hours exposed","96"="96 hours exposed")))+
                       ylab("Change in Swimming Velocity\n treatment vs control") + 
                       xlab("Bifenthirin Nominal Conc") +
                       scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                       theme_bw()
                          
  cntrlfishVel

# look at the change between 24 and 96 hours for each treamtent-spp
 
DataSum2496.vel$ExposureHrsChr = paste0("ExpHr",DataSum2496.vel$ExposureHrs)

DataSumChg.Vel = DataSum2496.vel %>%
  select(-index, -Trial, -Arena,-ExposureHrs) %>%
  pivot_wider(names_from=ExposureHrsChr, values_from=MnVel) %>%
  mutate(chngVel = ExpHr96 - ExpHr24) %>%
  data.frame()


  chngfishVel.box = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure") + 
                    xlab("Bifenthirin Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                    theme_bw()
  
  chngfishVel.box
  
  
  chngfishVel.py = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure)") + 
                  xlab("log(Bifenthirin Concentration (ng/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishVel.py
  
```
# the trends look the same as distance, so for now I won't run models on velocity. Can add later if needed. 





### Meander and Turn Angle
```{r meander/turn angle data, echo=F}
DataSum2496$TurnAngle_degRel2 = DataSum2496$SumTurnAngleRel
DataSum2496$TurnAngle_degRel2[DataSum2496$SumTurnAngleRel<0 &
                              !is.na(DataSum2496$SumTurnAngleRel)] <-
  DataSum2496$SumTurnAngleRel[DataSum2496$SumTurnAngleRel<0 &
                               !is.na(DataSum2496$SumTurnAngleRel)] + 360

## Summarize meander and turn angle
DataSum2496.meand = DataSum2496 %>%
  #filter(Meander>0.1) %>% # initially added this because many of the meander values are tiny and seem to be causing issues. Generally the fish move straight, but we want to know whether they turn more than normal, when they do turn. Perhaps should adjust all values < threshold to zero then run a zero inflated model on these. Predict the % of time they are moving straight (0) and then evaluate how much they are turning, if they turn. That will be a problem for a later day. 
  filter(SumTurnAngleAbs<360) %>% #these points are likely those where the fish stays still but the tracker jumps back and forth, making it look like a lot of 180 turns. They represent 0.48% of the dataset here for Bif 2020, at 24 and 96hrs
  filter(SumDistMoved>0) %>% # makes these plots only the metrics for when the fish is moving (ie: if fish moves, how straight does it move?)
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(SumTurnAngleRel))), 
            VarTurnAngle = deg(circ.disp.na(rad(SumTurnAngleRel))$var), # circ. variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSum2496.mraw = DataSum2496[!is.na(DataSum2496$TurnAngle_degRel2),]
```

```{r meander/turn angle plots, echo=F}
meanMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Mean Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

  
sdMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(SDMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Standard Deviation of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

CVMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(CVMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Coef-Var of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + ylim(c(0,100))+
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

  
mnTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Mean Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()


VarTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(VarTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Circular Variance of Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()


meanMeander.plot
sdMeander.plot # this plot seems to show the cleanest trends and the tightest boxes. why?
CVMeander.plot
mnTurnangle.plot
VarTurnangle.plot
```

```{r visualizing as distns of percent change in circular turn angle at 96}
DataSum96.ta = DataSum2496.meand[DataSum2496.meand$ExposureHrs==96,]

DataSum96.ta.cont = DataSum96.ta[DataSum96.ta$Treatment==0, c("Spp","ExposureHrs","Replicate","MnTurnAngle","VarTurnAngle")]
   DataSum96.ta.cont = rename(DataSum96.ta.cont,
                                 ControlMnTA = MnTurnAngle,
                                 ControlVarTA = VarTurnAngle)
   
DataSum96.ta.treat = DataSum96.ta[DataSum96.ta$Treatment!=0, c("Spp","ExposureHrs","Replicate","Treatment","MnTurnAngle","VarTurnAngle")]

DataSum96.ta.pseudowide = merge(DataSum96.ta.treat, DataSum96.ta.cont, all.x=T)

dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg96 = DataSum96.ta.pseudowide %>%
  group_by(Spp, Treatment, Replicate) %>%
  summarize(PercChgMn_TA = dist.func(a=ControlMnTA, b=MnTurnAngle),
            PercChgVar_TA = dist.func(a=ControlVarTA, b=VarTurnAngle)) %>%
           ungroup() %>% data.frame()

  PercChgMnTA.GSlm = lm(PercChgMn_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgMnTA.GSaov = aov(PercChgMnTA.GSlm)
    summary(PercChgMnTA.GSaov)
      TukeyHSD(PercChgMnTA.GSaov)
       # nothing is significantly different
     
    PercChgMnTA.WSlm = lm(PercChgMn_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgMnTA.WSaov = aov(PercChgMn.WSlm)
    summary(PercChgMnTA.WSaov)
      TukeyHSD(PercChgMnTA.WSaov)
       # nothing is significantly different
    
  PercChgVarTA.GSlm = lm(PercChgVar_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgVarTA.GSaov = aov(PercChgVarTA.GSlm)
    summary(PercChgVarTA.GSaov)
      TukeyHSD(PercChgVarTA.GSaov)
       # 2000 is significantly different than 5, 100, 500 @ p<0.05; nothing else
     
    PercChgVarTA.WSlm = lm(PercChgVar_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgVarTA.WSaov = aov(PercChgVarTA.WSlm)
    summary(PercChgVarTA.WSaov)
      TukeyHSD(PercChgVarTA.WSaov)
       # things are close but not significantly different
    
# are the boxes different from zero?      
onesamp.ttest <- PercChg96 %>%
  group_by(Spp, Treatment) %>%
  t_test(PercChgVar_TA~1) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance() %>%
  data.frame()
onesamp.ttest

DistnChgMnta.96= ggplot(PercChg96, 
                         aes(y=PercChgMn_TA, x=factor(Treatment),
                             fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, 
                                  linetype="dashed", color="black")+
                       geom_boxplot(outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                         scales="free" )+
                       geom_hline(yintercept = c(-0.5,0.5), lwd=.6, 
                              linetype="dashed", color="red") +
                       ylab("Change in Mean Turning Angle (deg)") + ylim(c(-6,6)) +
                       xlab("Bifenthrin Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgMnta.96


DistnChgVarTA.96= ggplot(PercChg96, 
                         aes(y=PercChgVar_TA, x=factor(Treatment),
                             fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, 
                                  linetype="dashed", color="black")+
                       geom_boxplot(outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       geom_hline(yintercept = c(0.5), lwd=.3, 
                              linetype="dashed", color="red") +
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                         scales="free" )+
                        ylab("Change in Circular Variance \nof Turn Angle (deg)") + 
                        ylim(c(-1,5)) +
                       xlab("Bifenthrin Nominal Concentration (ng/L)") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgVarTA.96

tiff("/Users/Anna/Documents/ResearchGit/SturgContam/figures/Exposure_OutputFigs/VarTA_Bif96_Perchg.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
DistnChgVarTA.96
dev.off()

```

```{r visualizing as distns of percent change in meander at 96}
DataSum96.meand = DataSum2496.meand[DataSum2496.meand$ExposureHrs==96,]

DataSum96.meand.cont = DataSum96.meand[DataSum96.meand$Treatment==0, c("Spp","ExposureHrs","Replicate","MnMeander","SDMeander")]
   DataSum96.meand.cont = rename(DataSum96.meand.cont,
                                 ControlMnMeander = MnMeander,
                                 ControlSDMeander = SDMeander)
   
DataSum96.meand.treat = DataSum96.meand[DataSum96.meand$Treatment!=0, c("Spp","ExposureHrs","Replicate","Treatment","MnMeander","SDMeander")]

DataSum96.meand.pseudowide = merge(DataSum96.meand.treat, DataSum96.meand.cont, all.x=T)

dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg96 = DataSum96.meand.pseudowide %>%
  group_by(Spp, Treatment, Replicate) %>%
  summarize(PercChgMn = dist.func(a=ControlMnMeander, b=MnMeander),
            PercChgSD = dist.func(a=ControlSDMeander, b=SDMeander)) %>%
           ungroup() %>% data.frame()

  PercChgMn.GSlm = lm(PercChgMn ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgMn.GSaov = aov(PercChgMn.GSlm)
    summary(PercChgMn.GSaov)
      TukeyHSD(PercChgMn.GSaov)
       # nothing is significantly different
     
    PercChgMn.WSlm = lm(PercChgMn ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgMn.WSaov = aov(PercChgMn.WSlm)
    summary(PercChgMn.WSaov)
      TukeyHSD(PercChgMn.WSaov)
       # nothing is significantly different
    
  PercChgSD.GSlm = lm(PercChgSD ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgSD.GSaov = aov(PercChgSD.GSlm)
    summary(PercChgSD.GSaov)
      TukeyHSD(PercChgSD.GSaov)
       # nothing is significantly different
     
    PercChgMn.WSlm = lm(PercChgMn ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgMn.WSaov = aov(PercChgMn.WSlm)
    summary(PercChgMn.WSaov)
      TukeyHSD(PercChgMn.WSaov)
       # nothing is significantly different
    

DistnChgMn.96.meand= ggplot(PercChg96, 
                         aes(y=PercChgMn, x=factor(Treatment), fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="black")+
                       geom_boxplot()+#outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free" )+
                       geom_hline(yintercept = c(-0.5,0.5), lwd=.6, 
                              linetype="dashed", color="red") +
                       ylab("Change in Mean Meander (deg/mm)") + #ylim(c(-50,1)) +
                       xlab("Bifenthrin Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgMn.96.meand


DistnChgSD.96.meand= ggplot(PercChg96, 
                         aes(y=PercChgSD, x=factor(Treatment), fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="black")+
                       geom_boxplot()+#outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free" )+
                       geom_hline(yintercept = c(-0.5,0.5), lwd=.6, 
                              linetype="dashed", color="red") +
                       ylab("Change in StDev of Meander (deg/mm)") + #ylim(c(-1,1)) +
                       xlab("Bifenthrin Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgSD.96.meand

# tiff("/Users/Anna/Documents/ResearchGit/SturgContam/figures/Exposure_OutputFigs/TrialDistance_Bif96_Perchg.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
# DistnChg96.dist
# dev.off()

```

### modelling for meander is in ExposureAnalysis3.rmd






### Time moving (distance moved > .5mm)
```{r active time data, echo=F }

#WS need longer distance to see trend; mm=2 is good
#GS need shorter distance to see trend; mm=.5 is good
threshold_mm=.5

DataSum2496 <- mutate(DataSum2496,
                active = ifelse(SumDistMoved > threshold_mm, 1, 0))

PlotData_propactive = DataSum2496 %>%
  group_by(Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(npos=n(), nactive = sum(active), propactive = sum(active)/n() ) %>%
  ungroup() %>%
  data.frame()
```

```{r active time plots, echo=F}

activefish = ggplot(PlotData_propactive, 
                           aes(fill=factor(Treatment), y=propactive, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(
    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
    #scales="free") +
  ylab("proportion with active movement") + 
  xlab("Exposure Hours") +#("Bifenthrin Nominal Conc.") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

activefish

```



## Sumarize time spent in center
```{r center zone data, echo=F} 
DataSum2496.centC = DataSum2496 %>%
  filter(!is.na(InZoneC)) %>%  ### will this bias the data if I remove those points where there isn't a detection? If the fish is more likely to be in the center when it's stationary, and it's more likely to be undetected when it's stationary, this may bias these values and under-represent the effect of the bifenthrin (more stationary when strongly affected)
  # also note, this line doesn't actually change the results because summing the InZoneC column drops all NA automatically; this line above just makes that explicit
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T), InZoneB = sum(InZoneB, na.rm=T), npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  mutate(PercZoneC.2 = InZoneC / (InZoneC+InZoneB)) %>%
  # ran this comparison to see how much the NA can influence the data, and it seems to be minor
  ungroup()  %>%
  data.frame()

```

```{r center zone plots, echo=F}

CenterC.plot = ggplot(DataSum2496.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()
CenterC.plot

ggplot(DataSum2496.centC, aes(x=PercZoneC.1, y=PercZoneC.2)) + geom_point(pch=21) + geom_abline(a=0,b=1, color="steelblue3") + facet_wrap(~Spp) + theme_bw()
```

These are some pretty good plots for WS. I think I'll use the distance moved (most intuitive), the turn angle, and the centerC plots. 

```{r presentation plots}
totfishdist
sdMeander.plot
activefish
CenterC.plot
```


```{r final summarized datasets for opendata}

DataSum2496$SumTurnAngleAbs = abs(DataSum2496$SumTurnAngleRel)
DataSum2496$MeanderCircAbs = abs(DataSum2496$MeanderCirc)

DataSum.summarized = DataSum2496 %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(Spp, Contaminant, ExposureHrs, Treatment, calcConc, 
           Replicate, RepID) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100),
            MnVel = mean(MnVel, na.rm=T),
            MnTurnAngle = deg(circ.mean.na(rad(SumTurnAngleAbs))), 
            VarTurnAngle = deg(circ.disp.na(rad(SumTurnAngleAbs))$var), # circular variance
            MnMeander = mean(MeanderCircAbs, na.rm=T),
            SDMeander = sd(MeanderCircAbs, na.rm=T),
            CVMeander = sd(MeanderCircAbs, na.rm=T)/abs(mean(MeanderCircAbs, na.rm=T)),
            InZoneC = sum(InZoneC, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

write.csv(DataSum.summarized, "/Users/Anna/Documents/ResearchGit/SturgContam/outputData/Exposure_Outputdata/Bifenthrin_2020_Cleaned_Conc_Summarized.csv")


```