---
title: "Exposure_Analysis2 - Exploratory Analysis"
author: "Anna Steel"
date: "9/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readtext) # need this because the ethovision output .txt files have unusual encoding as UTF-16
library(lme4)
library(circular)
#library(rethinking)
library(rprojroot) # only used for find_rstudio_root_file() to set project wd as root
library(rstatix)
library(chron)

knitr::opts_knit$set(root.dir = find_rstudio_root_file()) # sets root directory to match project directory, not rmd file location
```

```{r utility functions, include=FALSE}
# calculate hypotenuse of triangle created by two xy locations

distmov = function(x1,x2,y1,y2) { dm = sqrt((x1-x2)^2 + (y1-y2)^2); return(dm)}

# calculate number steps between detections; use summarized dataset (5 pos/sec)
nstep = function(t2,t1, interv=0.2) {
  if (t2-t1 < 0) stop('time steps backwards?')
  nstep <- ( (t2-t1) / interv)
  return(nstep)
  }


circ.mean.na = function(x) {
  x2 = x[!is.na(x)]
  sinr <- sum(sin(x2))
  cosr <- sum(cos(x2))
  circmean <- atan2(sinr, cosr)
  return(circmean)
}

circ.disp.na = function(x) {
  x2 = x[!is.na(x)]
    n <- length(x2)
    c <- sum(cos(x2))
    s <- sum(sin(x2))
    r <- sqrt(c^2 + s^2)
    rbar <- r/n
    var <- 1 - rbar
    data.frame(n, r, rbar, var)
}

```


## Read in Cleaned Data ("Exposure_Analysis1.Rmd")
```{r read in clean data}
#DataSum96.raw = read.csv("outputData/Exposure_Outputdata/Fipronil_2021_Cleaned_NoConc_96hrs.csv")
#DataSum2496.raw = read.csv("outputData/Exposure_Outputdata/Fipronil_2021_Cleaned_NoConc_2496hrs.csv")
DataSumAll.raw = read.csv("outputData/Exposure_Outputdata/Fipronil_2021_Cleaned_Conc_Allhrs.csv")
```


## Add measured concentrations (versus nominal)
```{r chem analysis results}
## is in Exposure_Analysis1_FIP@021, so removed here. Notes still valid

# chemcsv.raw = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/ChemAnalysis_Fipronil_2021_Summary.csv")
#   chemcsv <- chemcsv.raw[chemcsv.raw$chemical=="fipronil" & chemcsv.raw$sample=="spike", c("spp", "nomconc", "calcConc")]
#  
#   
# DataSum96 <- merge(DataSum96.raw, chemcsv, by.x=c("Spp","Treatment"), by.y=c("spp","nomconc"), all.x=T)
#  DataSum96$calcConc = as.numeric(DataSum96$calcConc)
#  
# DataSum2496 <- merge(DataSum2496.raw, chemcsv, by.x=c("Spp","Treatment"), by.y=c("spp","nomconc"), all.x=T)
#  DataSum96$calcConc = as.numeric(DataSum96$calcConc)
#  
# DataSumAll <- merge(DataSumAll.raw, chemcsv, by.x=c("Spp","Treatment"), by.y=c("spp","nomconc"), all.x=T)
#  DataSum96$calcConc = as.numeric(DataSum96$calcConc) 
 
```
# this uses 'spike' water analysis, and will report final composite sample in the paper. I think. Remember these were the chemical analysis results that were odd...likely because we used two seperate stock solutions for <100 and >500, which had been mixed by someone else and which were 2-3 months old when I used them. Used the same ones for both GS and WS, and they likely were degrading in the refridgerator between exposures. The best explanation for the chem results we saw was that there were high levels of degredate in the stock solution prior to initiation of the trial, leading to high levels for many of the chemical constituants for the 500 and 1000 ug/L exposures. 

## Add water temps at end of trial 
```{r add indiv water temp increase}
gstemp = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/Exposure_IndivBehaviorVideo_GS2021_Temps.csv")
wstemp = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/Exposure_IndivBehaviorVideo_WS2021_Temps.csv")

# interpolate missing temps 
tempdat = rbind(gstemp, wstemp)
tempdat$time <- times(paste0(tempdat$time, ":00"))

ggplot(data=tempdat, aes(x=time, y=endtemp)) + geom_point()

tempdat.redu = tempdat[!(tempdat$Exposure.Hr=="24" & tempdat$species=="WS" & tempdat$Tray %in% c("A","B","C","D")),] # legitimate notes for high temps for A,B, but also outliers for c,d if we're trying to make a high quality line for temp relationship with exposure video times
 ggplot(data=tempdat.redu, aes(x=time, y=endtemp)) + geom_point(aes(color=species))

templm = lm(endtemp ~ time + species, data=tempdat.redu)
 summary(templm) # temp = 6.83281 + 21.94528*time + 0.42187*WS + error
 plot(templm)

tempdat$pred.endtemp[tempdat$species=="GS"] = 6.83281 + 21.94528*tempdat$time[tempdat$species=="GS"]

tempdat$pred.endtemp[tempdat$species=="WS"] = 6.83281 + 21.94528*tempdat$time[tempdat$species=="WS"] + 0.42187

ggplot(tempdat, aes(x=endtemp, y=pred.endtemp, color=species)) + geom_point() + geom_line(data = data.frame(x=14:20, y=14:20), aes(x=x, y=y), color="black", lty=2)

#DataSum96.T = merge(DataSum96, tempdat, by.x=c("Spp","ExposureHrs","Tray","Replicate"), by.y=c("species","Exposure.Hr","Tray","rep"), all.x=T)
 # this uses the control as a sample for all of the corresponding replicate numbers
#DataSum96 = DataSum96.T

DataSumAll.T = merge(DataSumAll.raw, tempdat, 
                     by.x=c("Spp","ExposureHrs","Tray","Replicate"), 
                     by.y=c("species","Exposure.Hr","Tray","rep"), all.x=T)
 # this uses the control as a sample for all of the corresponding replicate numbers
```




## Exploratory Plots for each metric (Total distance travelled, Mean velocity, Meander and Turn angle, Use of center zone (% time), Time Active, Full Rotations vs distance traveled) 
  
  
### Distance  
  
```{r distance data, echo=F}

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum96.dist = DataSumAll.T %>%
  filter(ExposureHrs %in% c(96)) %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Tray, calcConc, Spp, RepID) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()


## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum2496.dist = DataSumAll.T %>%
  filter(ExposureHrs %in% c(24,96)) %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Tray, calcConc, Spp, RepID) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()


## Summarize for all timepoints to take total distance (sum moved in a trial) for each fish replicate
DataSumAll.dist = DataSumAll.raw %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Tray, calcConc, Spp, RepID) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()

```

```{r distance boxplots}
## with 96
totfishdist96_hist = ggplot(DataSum96.dist, aes(x=TotalfishDist_m) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(Treatment~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ #scales="free") +
                     theme_bw()

totfishdist96 = ggplot(DataSum96.dist, aes(fill=factor(Treatment), y=TotalfishDist_m, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~Spp, labeller = labeller(
                        Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),#)+
                        scales="free") +
                      ylab("Total Trial Distance (m)") + 
                      xlab("Exposure Hours") +
                      scale_fill_viridis_d(name="Nominal Fpironil\nConcentration (ug/L)") + 
                      theme_bw()

totfishdist96

## with 24 and 96
totfishdist_hist = ggplot(DataSum2496.dist, aes(x=TotalfishDist_m) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(Treatment~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ #scales="free") +
                     theme_bw()

totfishdist2496 = ggplot(DataSum2496.dist, aes(fill=factor(Treatment), y=TotalfishDist_m*100, x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~Spp, labeller = labeller(
                        Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")) )+
                        #scales="free") +
                      ylab("Total Trial Distance (cm)") + 
                      xlab("Exposure Hours") +
                      scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                      theme_bw()

totfishdist2496

tiff("figures/Exposure_OutputFigs/TotalDistance_Fip_GSWS_2496hrs.tiff", width=170, height=65, units="mm", compression="lzw", res=150)
totfishdist2496
dev.off()

### with all four timepoints
    totfishdistAll_hist = ggplot(DataSumAll.dist, aes(x=TotalfishDist_m) ) + 
                         geom_histogram(bins=15) + 
                         facet_wrap(Treatment~Spp, labeller = labeller(
                             Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ 
                         theme_bw()
    
    totfishdistAll = ggplot(DataSumAll.dist, aes(fill=factor(Treatment), y=TotalfishDist_m*100, 
                                   x=factor(ExposureHrs) ) ) + 
                          geom_boxplot(outlier.size = .75) + 
                          facet_wrap(~Spp, labeller = labeller(
                            Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),#)+
                            scales="free") +
                          ylab("Total Trial Distance (cm)") + 
                          xlab("Exposure Hours") +
                          scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                          theme_bw()
    
    totfishdistAll
    
    totfishdistAll_Control = ggplot(DataSumAll.dist[DataSumAll.dist$Treatment==0,], 
                                    aes(y=TotalfishDist_m, 
                                   x=factor(ExposureHrs),
                                   fill=Spp) ) + 
                          geom_boxplot(outlier.size = .75) + 
                          facet_wrap(~Spp, labeller = labeller(
                            Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
                          ylab("Total Trial Distance (m)") + 
                          xlab("Exposure Hours") +
                          scale_fill_manual(values=c("palegreen3","grey70"))+
                          theme_bw()
    
    totfishdistAll_Control
    
tiff("figures/Exposure_OutputFigs/TotalDistance_FipControl.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
totfishdistAll_Control
dev.off()
```

```{r visualizing as avg perc change of control}

 # look at the CHANGE between mean distance of control (mean for treatment-exposurehrs) because this is more standard for tox, and is how they define EC50 (50% change from control)
 # a little disappointing, because it loses all the variability by condensing to a mean and comparing, but that's how they do it I guess? 
 
AvgDistTreatmentAll = DataSumAll.dist %>%
 # subset(Treatment==0) %>%
  group_by(Spp, Treatment, ExposureHrs) %>%
  summarize(mean_dist = mean(TotalfishDist_m),
            median_dist =  median(TotalfishDist_m), n = n()) %>%
  ungroup %>% data.frame

MeanDist_PercChg = AvgDistTreatmentAll %>%
  pivot_wider(id_cols = c(ExposureHrs, Spp),
              names_from = Treatment, names_prefix="TotDistAt",
              values_from = mean_dist) %>%
  mutate(percdiff1 = (TotDistAt1 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff10 = (TotDistAt10 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff100 = (TotDistAt100 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff500 = (TotDistAt500 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff1000 = (TotDistAt1000 - TotDistAt0)/TotDistAt0) %>%
  pivot_longer(cols = c(percdiff1, percdiff10, percdiff100, percdiff500, percdiff1000),
               names_to = "Treatment",
               names_prefix = "percdiff",
              values_to = "PercDiff") %>%
  ungroup() %>% data.frame()
MeanDist_PercChg = MeanDist_PercChg[!duplicated(MeanDist_PercChg),]
MeanDist_PercChg$Treatment =  as.numeric(MeanDist_PercChg$Treatment)

MedianDist_PercChg = AvgDistTreatmentAll %>%
  pivot_wider(id_cols = c(ExposureHrs, Spp),
              names_from = Treatment, names_prefix="TotDistAt",
              values_from = median_dist) %>%
  mutate(percdiff1 = (TotDistAt1 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff10 = (TotDistAt10 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff100 = (TotDistAt100 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff500 = (TotDistAt500 - TotDistAt0)/TotDistAt0) %>%
  mutate(percdiff1000 = (TotDistAt1000 - TotDistAt0)/TotDistAt0) %>%
  pivot_longer(cols = c(percdiff1, percdiff10, percdiff100, percdiff500, percdiff1000),
               names_to = "Treatment",
               names_prefix = "percdiff",
              values_to = "PercDiff") %>%
  ungroup() %>% data.frame()
MedianDist_PercChg = MedianDist_PercChg[!duplicated(MedianDist_PercChg),]
MedianDist_PercChg$Treatment =  as.numeric(MedianDist_PercChg$Treatment)
              
  DiffMeanfishdist = ggplot(MeanDist_PercChg, 
                         aes(y=PercDiff, x=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="black")+
                       geom_col(fill="grey60") + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hrs", "48" = "48 hrs",
                                         "72" = "72 hrs", "96"="96 hrs")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="red")+
                       geom_hline(yintercept = (-0.2), lwd=.6, linetype="dashed", color="blue")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       theme_bw()
  DiffMeanfishdist
  
    DiffMedianfishdist = ggplot(MedianDist_PercChg, 
                         aes(y=PercDiff, x=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="black")+
                       geom_col(fill="grey60") + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hrs", "48" = "48 hrs",
                                         "72" = "72 hrs", "96"="96 hrs")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="red")+
                       geom_hline(yintercept = (-0.2), lwd=.6, linetype="dashed", color="blue")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       theme_bw()
                          
  DiffMedianfishdist  # saved for ppt as 600x550
```

```{r visualizing as distributions of percent change with All}

DataSumAll.dist.cont = DataSumAll.dist[DataSumAll.dist$Treatment==0, c("Spp","ExposureHrs","Replicate","Tray","TotalfishDist_m")]
   DataSumAll.dist.cont = rename(DataSumAll.dist.cont,
                                 ControlTotaldist = TotalfishDist_m)
   
DataSumAll.dist.treat = DataSumAll.dist[DataSumAll.dist$Treatment!=0, c("Spp","ExposureHrs","Replicate","Tray","calcConc","TotalfishDist_m")]

DataSumAll.dist.pseudowide = merge(DataSumAll.dist.treat, DataSumAll.dist.cont, all.x=T)

dist.dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg = DataSumAll.dist.pseudowide %>%
  group_by(Spp, ExposureHrs, calcConc, Replicate) %>%
  summarize(PercChg = dist.dist.func(a=ControlTotaldist, b=TotalfishDist_m)) %>%
           ungroup() %>% data.frame()


DistnChgfishdist = ggplot(PercChg, 
                         aes(y=PercChg, x=factor(calcConc)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="black")+
                       geom_boxplot(fill="grey60") + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hrs", "48" = "48 hrs",
                                         "72" = "72 hrs", "96"="96 hrs")) )+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="red")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       theme_bw()
DistnChgfishdist

MeanPercChgDistns = PercChg %>%
  group_by(Spp, ExposureHrs, calcConc) %>%
  summarize(mean_PercChg = mean(PercChg, na.rm=T), median_PercChg = median(PercChg, na.rm=T), sd_PercChg = sd(PercChg, na.rm=T)) %>%
  ungroup() %>% data.frame()



DistnChgfishdist.mean = ggplot(MeanPercChgDistns, 
                         aes(y=mean_PercChg, x=factor(calcConc)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_col(fill="grey60") + 
                       geom_errorbar(aes(ymin = mean_PercChg-sd_PercChg,
                                         ymax = mean_PercChg+sd_PercChg), width=.15)+
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hrs", "48" = "48 hrs",
                                         "72" = "72 hrs", "96"="96 hrs")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, 
                                  linetype="dashed", color="red")+
                      # geom_hline(yintercept = (-0.2), lwd=.6, 
                                  #linetype="dashed", color="blue")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       theme_bw()
DistnChgfishdist.mean


DistnChgfishdist.median = ggplot(MeanPercChgDistns, 
                         aes(y=median_PercChg, x=factor(calcConc)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_col(fill="grey60") + 
                       geom_errorbar(aes(ymin = median_PercChg-sd_PercChg,
                                         ymax = median_PercChg+sd_PercChg), width=.15)+
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hrs", "48" = "48 hrs",
                                         "72" = "72 hrs", "96"="96 hrs")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, 
                                  linetype="dashed", color="red")+
                       #geom_hline(yintercept = (-0.2), lwd=.6, 
                                  linetype="dashed", color="blue")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       theme_bw()
DistnChgfishdist.median


```
```{r visualizing as distributions of percent change with 96}

DataSum96.dist.cont = DataSum96.dist[DataSum96.dist$Treatment==0, c("Spp","ExposureHrs","Replicate","Tray","TotalfishDist_m")]
   DataSum96.dist.cont = rename(DataSum96.dist.cont,
                                 ControlTotaldist = TotalfishDist_m)
   
DataSum96.dist.treat = DataSum96.dist[DataSum96.dist$Treatment!=0, c("Spp","ExposureHrs","Replicate","Tray","calcConc","TotalfishDist_m")]

DataSum96.dist.pseudowide = merge(DataSum96.dist.treat, DataSum96.dist.cont, all.x=T)
# note: mean distance moved for GS control was  8.07m over the 12 minutes of obs
# note: mean distance moved for WS control was 22.01m over the 12 minutes of obs

dist.dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg96 = DataSum96.dist.pseudowide %>%
  group_by(Spp, calcConc, Replicate) %>%
  summarize(PercChg = dist.dist.func(a=ControlTotaldist, b=TotalfishDist_m)) %>%
           ungroup() %>% data.frame()

    PercChgGSlm = lm(PercChg ~ factor(calcConc), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgGSaov = aov(PercChgGSlm)
    summary(PercChgGSaov)
      TukeyHSD(PercChgGSaov)
       # nothing is significantly different
     
    PercChgWSlm = lm(PercChg ~ factor(calcConc), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgWSaov = aov(PercChgWSlm)
    summary(PercChgWSaov)
      TukeyHSD(PercChgWSaov)
       # difference between 1000 and all others is significant @ p<0.01; nothing else
    
          
# are the boxes different from zero?      
onesamp.ttest <- PercChg96 %>%
  group_by(Spp, calcConc) %>%
  t_test(PercChg~1) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance() %>%
  data.frame()
onesamp.ttest
 # only WS 1000 is different from control
      
    
DistnChg96.dist = ggplot(PercChg96, 
                         aes(y=PercChg, x=factor(calcConc), fill=factor(calcConc)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="black")+
                       geom_boxplot(outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")) )+
                       geom_hline(yintercept = (-0.5), lwd=.6, linetype="dashed", color="red")+
                       ylab("Change in Swimming Distance (m)") + ylim(c(-1,1)) +
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChg96.dist

tiff("/Users/Anna/Documents/ResearchGit/SturgContam/figures/Exposure_OutputFigs/TrialDistance_Fip96_Perchg.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
DistnChg96.dist
dev.off()

```
```{r visualizing as avg of distributions of percent change with 96}
AvgPercChg96.dist = PercChg96 %>%
  group_by(Spp, calcConc) %>%
  summarize(mean_PercChg = mean(PercChg, na.rm=T), 
            median_PercChg = median(PercChg, na.rm=T), 
            sd_PercChg = sd(PercChg, na.rm=T),
            n=n() ) %>%
  ungroup() %>% data.frame()
AvgPercChg96.dist$se_PercChg = AvgPercChg96.dist$sd_PercChg /AvgPercChg96.dist$n 


DistnChgfish.dist.mean = ggplot(AvgPercChg96.dist, 
                         aes(y=mean_PercChg, x=factor(calcConc), fill=Spp) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_errorbar(aes(ymin = mean_PercChg-sd_PercChg,
                                         ymax = mean_PercChg+sd_PercChg), width=.25)+
                       geom_point(size=5, pch=21) + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, 
                                  linetype="dashed", color="red")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_manual(values=c("palegreen3","grey70")) + 
                       theme_bw()
DistnChgfish.dist.mean


DistnChgfish.dist.median = ggplot(AvgPercChg96.dist, 
                         aes(y=median_PercChg, x=factor(calcConc), fill=Spp) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_errorbar(aes(ymin = median_PercChg-sd_PercChg,
                                         ymax = median_PercChg+sd_PercChg), width=.25)+
                       geom_point(size=5, pch=21) + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, 
                                  linetype="dashed", color="red")+
                        ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       scale_fill_manual(values=c("palegreen3","grey70")) + 
                       theme_bw()
DistnChgfish.dist.median




DistnChgfish.dist.mean = ggplot(AvgPercChg96.dist, 
                         aes(y=mean_PercChg, x=factor(calcConc), fill=Spp) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_col() + 
                       geom_errorbar(aes(ymin = mean_PercChg-sd_PercChg,
                                         ymax = mean_PercChg+sd_PercChg), width=.25)+
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, 
                                  linetype="dashed", color="red")+
                       ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_manual(values=c("palegreen3","grey70")) + 
                       theme_bw()
DistnChgfish.dist.mean


DistnChgfish.dist.median = ggplot(AvgPercChg96.dist, 
                         aes(y=median_PercChg, x=factor(calcConc), fill=Spp) ) + 
                       geom_hline(yintercept = 0, lwd=.6, color="black")+
                       geom_boxplot() + 
                       #geom_errorbar(aes(ymin = median_PercChg-sd_PercChg,
                       #                  ymax = median_PercChg+sd_PercChg), width=.25)+

                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                       geom_hline(yintercept = (-0.5), lwd=.6, 
                                  linetype="dashed", color="red")+
                        ylab("Percent Change in Swimming Distance (m)") + 
                       xlab("Fipronil Nominal Conc") +
                       scale_fill_manual(values=c("palegreen3","grey70")) + 
                       theme_bw()
DistnChgfish.dist.median


```
  
```{r diff btwn 24 and 96hrs}  
# look at the change between 24 and 96 hours for each replicated individual
 
DataSum2496.dist$ExposureHrsChr = paste0("ExpHr",DataSum2496.dist$ExposureHrs)
DataSum2496.dist$lnCalcConc = log(DataSum2496.dist$calcConc+1)

DataSumChg.dist = DataSum2496.dist %>%
  pivot_wider(id_cols = c(RepID, Treatment, Spp, Replicate, calcConc, lnCalcConc), 
              names_from = ExposureHrs, names_prefix="TotDistAt", 
              values_from = TotalfishDist_m) %>%
  mutate(chngdist = TotDistAt96 - TotDistAt24) %>%
  data.frame



  chngfishdist.box = ggplot(DataSumChg.dist, 
                           aes(y=chngdist/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Distance\nfrom 24 to 96 hrs of exposure (m)") + 
                    xlab("Fipronil Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                    theme_bw()
  
  chngfishdist.box
  
  
  chngfishdist.py = ggplot(DataSumChg.dist, 
                           aes(y=chngdist/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Distance\nfrom 24 to 96 hrs of exposure (m)") + 
                  xlab("log(Fipronil Concentration (ug/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishdist.py
```  
  
# do individuals consistently respond in the same way? Should I add a multilevel term for intercept or slope. Or both?
```{r individual repeatability}  
ggplot(DataSum2496.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=RepID)) + geom_point() + geom_line() + facet_grid(Spp~Treatment, scales="free") + theme(legend.position="none")
# looks like there is often a trend, but not always. I think a random slope between the two time points would be really helpful. 


ggplot(DataSumAll.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=RepID)) + geom_point() + geom_line() + facet_grid(Spp~Treatment, scales="free") + theme(legend.position="none")
# when we include all four timepints this gets really messy; probably can't (shouldn't) do a random effect for exposure time if I include all these timepoints. 

ggplot(DataSumAll.dist[DataSumAll.dist$ExposureHrs%in% c(48,96),], aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=RepID)) + geom_point() + geom_line() + facet_grid(Spp~Treatment, scales="free") + theme(legend.position="none")
# when we include all four timepints this gets really messy; probably can't (shouldn't) do a random effect for exposure time if I include all these timepoints. 

ggplot(DataSum2496.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=Spp)) + geom_point() + geom_line() + facet_grid(Treatment~Replicate, scales="free") + theme_bw() + theme(legend.position="none")

ggplot(DataSumAll.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=Spp)) + geom_point() + geom_line() + facet_grid(Treatment~Replicate, scales="free") + theme_bw() + theme(legend.position="none")

```

### modelling for distance is in ExposureAnalysis3.rmd





### Velocity 
```{r velocity data, echo=F}

## Summarize movement velocity
 
DataSum2496.vel = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  summarize(MnVel = mean(MnVel, na.rm=T), npos = n()) %>%
  ungroup()  %>%
  data.frame()
```

```{r velocity plots}

MoveVel.plot = ggplot(DataSum2496.vel, 
                           aes(fill=factor(Treatment), y=MnVel, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Mean movement velocity (mm/s)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

MoveVel.plot
```

```{r other ways of visualizing velocity}

 # look at the CHANGE between mean vel of control (mean for treatment-exposurehrs) and target conc (each individual)
 
MeanVel0 = DataSum2496.vel %>%
  subset(Treatment==0) %>%
  group_by(Spp, ExposureHrs) %>%
  summarize(mean0_Vel = mean(MnVel)) %>%
  ungroup %>% data.frame

DataSumDiff.Vel = merge(DataSum2496.vel, MeanVel0, all.x=T)

DataSumDiff.Vel$VelDiff = DataSumDiff.Vel$MnVel - DataSumDiff.Vel$mean0_Vel


  cntrlfishVel = ggplot(DataSumDiff.Vel, 
                         aes(y=VelDiff/10, x=factor(Treatment),fill=factor(Treatment) ) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                       geom_boxplot(outlier.size = .75) + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hours exposed","96"="96 hours exposed")))+
                       ylab("Change in Swimming Velocity\n treatment vs control") + 
                       xlab("Fipronil Nominal Conc") +
                       scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                       theme_bw()
                          
  cntrlfishVel

# look at the change between 24 and 96 hours for each treamtent-spp
 
DataSum2496.vel$ExposureHrsChr = paste0("ExpHr",DataSum2496.vel$ExposureHrs)

DataSumChg.Vel = DataSum2496.vel %>%
  select(-index, -Trial, -Arena,-ExposureHrs) %>%
  pivot_wider(names_from=ExposureHrsChr, values_from=MnVel) %>%
  mutate(chngVel = ExpHr96 - ExpHr24) %>%
  data.frame()


  chngfishVel.box = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure") + 
                    xlab("Fipronil Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                    theme_bw()
  
  chngfishVel.box
  
  
  chngfishVel.py = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure)") + 
                  xlab("log(Fipronil Concentration (ug/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishVel.py
  
```
# the trends look the same as distance, so for now I won't run models on velocity. Can add later if needed. 






### Meander and Turn Angle

```{r meander/turn angle data, echo=F}

## Summarize meander and turn angle
DataSum96.meand = DataSum96 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp) %>%#, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(TurnAngleCirc))), 
            VarTurnAngle = deg(circ.disp.na(rad(TurnAngleCirc))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSum96.mraw = DataSum96[!is.na(DataSum96$TurnAngle_deg),]


## Summarize meander and turn angle
DataSum2496.meand = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(TurnAngleCirc))), 
            VarTurnAngle = deg(circ.disp.na(rad(TurnAngleCirc))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSum2496.mraw = DataSum2496[!is.na(DataSum2496$TurnAngle_deg),]



## Summarize meander and turn angle
DataSumAll.meand = DataSumAll %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))), 
            VarTurnAngle = deg(circ.disp.na(rad(abs(SumTurnAngleRel)))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSumAll.mraw = DataSumAll[!is.na(DataSumAll$TurnAngle_deg),]
```

```{r meander/turn angle plots 2496, echo=F}
meanMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
mnTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
sdMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(SDMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Standard Deviation of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

CVMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(CVMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Coef-Var of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + ylim(c(0,100))+
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

VarTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(VarTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Circular Variance of Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()


meanMeander.plot
sdMeander.plot # this plot seems to show the cleanest trends and the tightest boxes. why?
CVMeander.plot
mnTurnangle.plot
VarTurnangle.plot
```

```{r meander/turn angle plots All, echo=F}
meanMeander.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=abs(MnMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
mnTurnangle.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=abs(MnTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
sdMeander.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=(SDMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Standard Deviation of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

CVMeander.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=(CVMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Coef-Var of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + ylim(c(0,100))+
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

VarTurnangle.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=(VarTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Circular Variance of Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()


meanMeander.plot
sdMeander.plot # this plot seems to show the cleanest trends and the tightest boxes. why?
CVMeander.plot
mnTurnangle.plot
VarTurnangle.plot
```

```{r visualizing as distns of percent change in circular turn angle at 96}
DataSum96.ta = DataSum96.meand

DataSum96.ta.cont = DataSum96.ta[DataSum96.ta$Treatment==0, c("Spp","ExposureHrs","Replicate","MnTurnAngle","VarTurnAngle")]
   DataSum96.ta.cont = rename(DataSum96.ta.cont,
                                 ControlMnTA = MnTurnAngle,
                                 ControlVarTA = VarTurnAngle)
   
DataSum96.ta.treat = DataSum96.ta[DataSum96.ta$Treatment!=0, c("Spp","ExposureHrs","Replicate","Treatment","MnTurnAngle","VarTurnAngle")]

DataSum96.ta.pseudowide = merge(DataSum96.ta.treat, DataSum96.ta.cont, all.x=T)

dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg96 = DataSum96.ta.pseudowide %>%
  group_by(Spp, Treatment, Replicate) %>%
  summarize(PercChgMn_TA = dist.func(a=ControlMnTA, b=MnTurnAngle),
            PercChgVar_TA = dist.func(a=ControlVarTA, b=VarTurnAngle)) %>%
           ungroup() %>% data.frame()
PercChg96$Treatment = factor(PercChg96$Treatment)

  PercChgMnTA.GSlm = lm(PercChgMn_TA ~ Treatment, 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgMnTA.GSaov = aov(PercChgMnTA.GSlm)
    summary(PercChgMnTA.GSaov)
      emmeans(PercChgMnTA.GSlm, specs="Treatment") # dif from 0?
      TukeyHSD(PercChgMnTA.GSaov) # dif from eachother?
       # nothing is significantly different
     
    PercChgMnTA.WSlm = lm(PercChgMn_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgMnTA.WSaov = aov(PercChgMnTA.WSlm)
    summary(PercChgMnTA.WSaov)
      emmeans(PercChgMnTA.WSlm, specs="Treatment") # dif from 0?
      TukeyHSD(PercChgMnTA.WSaov)
       # nothing is significantly different
    
  PercChgVarTA.GSlm = lm(PercChgVar_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgVarTA.GSaov = aov(PercChgVarTA.GSlm)
    summary(PercChgVarTA.GSaov)
      TukeyHSD(PercChgVarTA.GSaov)
       # nothing is significantly different
     
    PercChgVarTA.WSlm = lm(PercChgVar_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgVarTA.WSaov = aov(PercChgVarTA.WSlm)
    summary(PercChgVarTA.WSaov)
      TukeyHSD(PercChgVarTA.WSaov)
       # nothing is significantly different from the other treatments
    
      
# are the boxes different from zero?      
onesamp.ttest <- PercChg96 %>%
  group_by(Spp, Treatment) %>%
  t_test(PercChgVar_TA~1) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance() %>%
  data.frame()
onesamp.ttest

      

DistnChgMnta.96= ggplot(PercChg96, 
                         aes(y=PercChgMn_TA, x=factor(Treatment),
                             fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, 
                                  linetype="dashed", color="black")+
                       geom_boxplot()+#outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                         scales="free" )+
                       geom_hline(yintercept = c(-0.5,0.5), lwd=.6, 
                              linetype="dashed", color="red") +
                       ylab("Change in Mean Turning Angle (deg)") + #ylim(c(-6,6)) +
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgMnta.96


DistnChgVarTA.96= ggplot(PercChg96, 
                         aes(y=PercChgVar_TA, x=factor(Treatment),
                             fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, 
                                  linetype="dashed", color="black")+
                      geom_hline(yintercept = c(-0.5, 0.5), lwd=.3, 
                              linetype="dashed", color="red") +
                        geom_boxplot(outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                         scales="free" )+
                       ylab("Change in Circular Variance \nof Turn Angle (deg)") + 
                        ylim(c(-1,1)) +
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgVarTA.96


tiff("/Users/Anna/Documents/ResearchGit/SturgContam/figures/Exposure_OutputFigs/VarTA_Fip96_Perchg.tiff", width=142, height=70, units="mm", compression="lzw", res=150)
DistnChgVarTA.96
dev.off()

```


### modelling for meander is in ExposureAnalysis3.rmd






### Time moving (distance moved > .5mm)
```{r active time data, echo=F }

#WS need longer distance to see trend; mm=2 is good
#GS need shorter distance to see trend; mm=.5 is good
threshold_mm=.5

DataSum2496 <- mutate(DataSum2496,
                active = ifelse(SumDistMoved > threshold_mm, 1, 0))

PlotData_propactive = DataSum2496 %>%
  group_by(Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(npos=n(), nactive = sum(active), propactive = sum(active)/n() ) %>%
  ungroup() %>%
  data.frame()
```

```{r active time plots, echo=F}

activefish = ggplot(PlotData_propactive, 
                           aes(fill=factor(Treatment), y=propactive, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(
    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
    #scales="free") +
  ylab("proportion with active movement") + 
  xlab("Exposure Hours") +#("Fipronil Nominal Conc.") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

activefish

```





### Sumarize time spent in center
```{r center zone data, echo=F} 
DataSum2496.centC = DataSumAll.raw %>%
  filter(ExposureHrs %in% c(24,96)) %>%
  filter(!is.na(InZoneC)) %>%  ### will this bias the data if I remove those points where there isn't a detection? If the fish is more likely to be in the center when it's stationary, and it's more likely to be undetected when it's stationary, this may bias these values and under-represent the effect of the Fipronil (more stationary when strongly affected)
  # also note, this line doesn't actually change the results because summing the InZoneC column drops all NA automatically; this line above just makes that explicit
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID, Tray) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T),# InZoneB = sum(InZoneB, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  #mutate(PercZoneC.2 = InZoneC / (InZoneC+InZoneB)) %>%
  # ran this comparison to see how much the NA can influence the data, and it seems to be minor
  ungroup()  %>%
  data.frame()


DataSumAll.centC = DataSumAll.raw %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID, Tray) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T), npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

```

```{r center zone plots, echo=F}

CenterC.plot2496 = ggplot(DataSum2496.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions\nin Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
CenterC.plot2496


tiff("figures/Exposure_OutputFigs/PercZone_Fip_GSWS_2496hr.tiff", width=170, height=65, units="mm", compression="lzw", res=150)
CenterC.plot2496
dev.off()




CenterCAll.plot = ggplot(DataSumAll.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
CenterCAll.plot

tiff("figures/Exposure_OutputFigs/PercZone_Fip_GSWS_Allhrs.tiff", width=140, height=45, units="mm", compression="lzw", res=150)
CenterCAll.plot
dev.off()



```

These are some pretty good plots for WS. I think I'll use the distance moved (most intuitive), the turn angle, and the centerC plots. 

```{r presentation plots}
totfishdist
sdMeander.plot
activefish
CenterC.plot
```

```{r final summarized datasets for opendata}

DataSumAll.summarized = DataSumAll.T %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(Spp, Contaminant, ExposureHrs, Treatment, calcConc, 
           Tray, Replicate, index, RepID, endtemp, pred.endtemp) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100),
            MnVel = mean(MnVel, na.rm=T),
            MnTurnAngle = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))), 
            VarTurnAngle = deg(circ.disp.na(rad(abs(SumTurnAngleRel)))$var), # circ. var.
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)),
            InZoneC = sum(InZoneC, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

write.csv(DataSumAll.summarized, "/Users/Anna/Documents/ResearchGit/SturgContam/outputData/Exposure_Outputdata/Fipronil_2021_Cleaned_Conc_Summarized.csv")


```