---
title: "Exposure_Mortality_Allyrs"
author: "Anna Steel"
date: "2023-09-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(MuMIn)
library(tidyverse)
library(gtsummary) # for making beautiful tables of raw datasets and of glm outputs; builds off gt package

# set wd to the location of the project, not the script file
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```


## read in compiled mortality data for plots for presentations
```{r read in data, echo=FALSE}

mdat = read.csv("rawData/ExposureCompiled_Mortality_Summary.csv")

 mdat$notes = NULL
 str(mdat)
 #mdat$spp = factor(mdat$spp)
 mdat$RepDish = factor(mdat$RepDish)
 #mdat$conclevel = factor(mdat$conclevel)
 
 mdat$lognomconc = log(mdat$nomconc+1)
 
# remove top to concentrations for fipronil (both spp) 
mdat = mdat[!(mdat$nomconc %in% c(500,1000) & mdat$contaminant=="fipronil"),]

# copy these values into an excel table for report
mdat_summary <- mdat %>%
  filter(year%in% c(2022,2023))%>%
  group_by(spp, contaminant, nomconc, tempC) %>%
   summarize(mean.perc.mort = mean(perc.mort),
            se.perc.mort = sd(perc.mort, na.rm=TRUE)/n(),
            ndish = n(),
            total.exposure.morts = sum(total.exposure.morts),
            nfish = sum(total.accounted.for) ) %>%
  data.frame()



## read in chem analysis numbers
chemanaly = read.csv("rawData/ChemAnalysisResults_CompiledforR.csv")
 chemanaly$CalcConc[chemanaly$CalcConc=="ND"] <- 0
 names(chemanaly) <- tolower(names(chemanaly))
 chemanaly$contaminant <- tolower(chemanaly$contaminant)

 
```
```{r  wasted attempt to make pretty tables with gt or gtsummary, Not helpful tools, may return someday, echo=FALSE, eval=FALSE}
# tried  to make a beautiful table uysing gtsummary
# mdat_summary <- mdat %>%
#   group_by(spp, contaminant, nomconc, tempC) %>%
#    summarize(mean.perc.mort = mean(perc.mort), 
#             se.perc.mort = sd(perc.mort, na.rm=TRUE)/n(),
#             ndish = n(),
#             total.exposure.morts = sum(total.exposure.morts),
#             nfish = sum(total.accounted.for) ) %>%
#   data.frame()
# 
# mdat_summary$se.perc.mort[is.na(mdat_summary$se.perc.mort)] <- 0 # can't figure out how to do this in a pipe

### epic fail
# mdat_table_fip <- mdat_summary %>%
#   filter(contaminant=="fipronil") %>%
#   select(spp, nomconc, mean.perc.mort, nfish, nfish) %>%
#   tbl_strata2( strata = spp,
#               .tbl_fun = 
#                 ~ .x %>%
#                 tbl_summary(by = nomconc) ) %>%
#   bold_labels()
#   

### the time investment is huge and out pa off is tiny. Ending this wasted time persuit  
# mdat_fip_wide.mort <- mdat_summary %>%
#    filter(contaminant=="fipronil") %>%
#    select(spp, nomconc, mean.perc.mort) %>%
#    spread(key=nomconc, value=mean.perc.mort)
# 
# mdat_table_fip <- mdat_summary %>%
#    filter(contaminant=="fipronil") %>%
#    select(spp, nomconc, mean.perc.mort, nfish, nfish) %>%
#    gt() %>%
#     tab_header(title="Acute Mortality, Fipronil") %>%
#     tab_spanner(label="Nominal Concentration",
#                 columns = 
#     strata = tempC,
#               .tbl_fun = 
#                 ~ .x %>%
#                 tbl_summary(by = tempC, missing="no"),
#               .header="**{strata}**C" ) %>%
#   bold_labels()


```



## comparision 1 -> concentrations using WS fip and bif range test (15C) 
```{r compare WS by contam, echo=FALSE}
conc.comp <- mdat %>%
   filter(spp=="WS") %>%
   filter(tempC==15) %>%
   #filter(year %in% c(2020, 2021)) %>%
   data.frame()
   
 ggplot(data=conc.comp, 
        aes(x=factor(nomconc), y=perc.mort, fill=contaminant)) + 
   geom_boxplot() + facet_wrap(~contaminant, scales="free") + 
     theme_bw()
 
 # summarize to get mean mortality perc by concentration and contaminant
 conc.sum <- conc.comp %>%
   group_by(spp, contaminant, color, conclevel) %>%
   summarize(mean.perc.mort = mean(perc.mort), se.perc.mort = sd(perc.mort)/n() ) %>%
   data.frame()
 conc.sum$se.perc.mort[is.na(conc.sum$se.perc.mort)] <- 0
 #conc.sum$conclevel[conc.sum$contaminant=="fipronil"] <- conc.sum$conclevel+0.1
 
add.nomconc = data.frame(contaminant = rep(c("bifenthrin","fipronil"), each=6),
                         conclevel = rep(c(0:5), times=2),
                         nomconc = c(0,10,100,500,1000,2000, 0,1,10,100,500,1000))
conc.sum = merge(conc.sum, add.nomconc, all.x=T)
 
 mean.mort.plot1 = ggplot(data=conc.sum, aes(x=log(nomconc+1), y=mean.perc.mort, fill=contaminant)) + 
   geom_errorbar(aes(ymin = mean.perc.mort - se.perc.mort, 
                     ymax = mean.perc.mort + se.perc.mort)) + 
   geom_point(pch=21, size=3) + 
   facet_grid(spp~contaminant, scales="free", 
              labeller = labeller(contaminant = c("bifenthrin" = "Bifenthrin, ng/L",
                                                  "fipronil" = "Fipronil, ug/L")) ) + 
   scale_fill_manual(values=c("rosybrown1","salmon2"), guide="none") + 
  scale_x_continuous(name = "Nominal Pesticide Concentration", breaks = log(c(0,10,100,1000,10000)+1), labels=c(0,10,100,1000,10000) ) + 
   theme_bw() 
 
 # mean.mort.plot1 + scale_y_continuous(name = "Mean Mortality", breaks = seq(0,.5,.1), labels=paste0(seq(0,50,10), "%"), limits=c(0,.5) )

 mean.mort.plot1 + scale_y_continuous(name = "Mean Mortality", breaks = seq(0,.1,.02), labels=paste0(seq(0,10,2), "%"), limits = c(0,.1)) 

tiff("figures/Mortality_WS_contaminantComp_forpresentation.jpeg",  width=600, height=300, units="px", compression="lzw", res=100)
 mean.mort.plot1 + scale_y_continuous(name = "Mean Mortality", breaks = seq(0,.1,.02), labels=paste0(seq(0,10,2), "%"), limits = c(0,.1)) 
dev.off()
```

## stats for WS by pesticide (comp 1)
```{r WS comparison1 stats, echo=FALSE}
chemanaly.WS = filter(chemanaly, spp=="WS", sample=="spike")
#chemanaly.WS = filter(chemanaly.WS, !(contaminant %in% c("fipronil desulfinyl",
#                                                    "desulfinyl fipronil amide",
#                                                    "fipronil amide")))

conc.comp <- mdat %>%
   filter(spp=="WS") %>%
   filter(tempC==15) %>%
   data.frame()

conc.comp2 = merge(conc.comp, chemanaly.WS, all.X=T)
 conc.comp2$calcconc <- as.numeric(conc.comp2$calcconc)

conc.comp2$logcalcconc = log(conc.comp2$calcconc+1)                  



comp.lm = lm(perc.mort ~ contaminant*logcalcconc , data=conc.comp2) # ignores the byproducts of fipronil
plot(comp.lm) # not good residuals
summary(comp.lm) 

# when doing a glm binomial, the LHS is a two column matrix witrh N success and N failures
comp.glm = glm(cbind(total.exposure.morts, final.tally) ~ contaminant*logcalcconc, data=conc.comp2, family="binomial", na.action=na.fail)
plot(comp.glm) # qq plot isn't good either, but I think that's okay for binomials?
summary(comp.glm)
dredge(comp.glm) # best model is with no predictors. =) That's funny. Next best is with contaminant


      # library(rethinking)
      # 
      # concCompBayes = conc.comp
      # names(concCompBayes)[c(9,10,11,12,13)]  <- c("ExposMort","IncidentMort","FinalTally","TotalFish","PercMort")
      # concCompBayes$FishTested = concCompBayes$ExposMort + concCompBayes$FinalTally
      # 
      # compBayesBinom <- map2stan(
      #         alist(
      #               ExposMort ~ dbinom(TotalFish,p),
      #             logit(p) <-a + bC*contaminant + bLNC*lognomconc + bCLNC*contaminant*lognomconc, 
      #               a ~ dnorm(0,10),
      #               c(bC, bLNC, bCLNC) ~ dnorm(0,10)
      #            ), 
      #            data = concCompBayes, chains=4, warmup=500, iter=1500) 
      #       plot(compBayesBinom); precis(compBayesBinom)
      # 
      # 
      # compBayesPoission <- map2stan(
      #         alist(
      #               ExposMort ~ dpois(p),
      #         log(p) <- FishTested + a + bC*contaminant + bLNC*lognomconc + bCLNC*contaminant*lognomconc, 
      #               a ~ dnorm(0,10),
      #               c(bC, bLNC, bCLNC) ~ dnorm(0,10)
      #            ), 
      #            data = concCompBayes, chains=4, warmup=500, iter=1500) 
      #       plot(compBayesPoission); precis(compBayesPoission)

```



## comparison 2 -> multiple stressors, WS/GS bifenthrin at temp
```{r WS/GS comparing2 mort by temp, echo=FALSE}
 conc.comp2 <- mdat %>%
   #filter(spp=="WS") %>%
   filter(year %in% c(2022, 2023)) %>%
   data.frame()
   
 #plot raw data for each dish
 ggplot(data=conc.comp2, 
        aes(x=factor(nomconc), y=perc.mort, fill=factor(tempC)) ) + 
   geom_point(pch=21, size=3, position="jitter") + 
   facet_grid(spp~tempC)+#, scales="free") + 
   scale_fill_discrete(guide="none")+
     theme_bw()
 
 # plot summarized data for each treatment
 conc.sum2 <- conc.comp2 %>%
   group_by(spp, tempC, color, conclevel) %>%
   summarize(mean.perc.mort = mean(perc.mort), 
             se.perc.mort = sd(perc.mort)/n(), 
             nrep = n(), 
             nfish = sum(total.accounted.for) ) %>%
   data.frame()
     conc.sum2$se.perc.mort[is.na(conc.sum2$se.perc.mort)] <- 0
     add.nomconc2 = data.frame(conclevel = 0:5,
                         nomconc = c(0,10,100,500,1000,2000) )
     conc.sum2 = merge(conc.sum2, add.nomconc2, all.x=T)

 # basic plot
 mean.mort.plot2 = ggplot(data=conc.sum2, aes(x=log(nomconc+1), y=mean.perc.mort, fill=factor(spp))) + 
   geom_errorbar(aes(ymin = mean.perc.mort - se.perc.mort, 
                     ymax = mean.perc.mort + se.perc.mort,
                     width=0.75)) + 
   geom_point(pch=21, size=2) + 
   facet_grid(spp~tempC, #scales="free", 
              labeller = labeller(tempC = c("12"="12C", "15"="15C", "18"="18C")) ) + 
   scale_fill_manual(values=c("green3","grey80"), guide="none") + 
   #scale_fill_manual(values=c("turquoise1","turquoise3","turquoise4"), guide="none") +
   scale_x_continuous(name = "Bifenthrin Concentration (ng/L)",
                      breaks = log(c(0,10,100,1000)+1),                                               labels=c(0,10,100,1000) ) + 
   theme_bw() 
 
 # plot with y-scale from 0-50%
 mean.mort.plot2 + scale_y_continuous(name = "Mean Mortality (%)", 
                                      breaks = seq(0,.5,.1), 
                                      labels = seq(0,50,10), 
                                      limits=c(0,.5) )
 # plot with y-scale from 0-10%
 mean.mort.plot2 + scale_y_continuous(name = "Mean Mortality (%)", 
                                      breaks = seq(0,.1, .02), 
                                      labels=seq(0,10,2), 
                                      limits=c(0,.1) ) 

# tiff("figures/Mortality_GSWS_bifbytemp_forreport.jpeg",  width=600, height=300, units="px", compression="lzw", res=100)
#  mean.mort.plot2 + scale_y_continuous(name = "Mean Mortality (%)", breaks = seq(0,.1,.02), labels=seq(0,10,2), limits = c(0,.1)) 
# dev.off()
```

```{r WS/GS comparing2 deformed by temp, echo=FALSE}
 conc.comp2 <- mdat %>%
   filter(year %in% c(2022, 2023)) %>%
   data.frame()
   

 # plot summarized data for each treatment
 conc.sum2.def <- conc.comp2 %>%
   mutate(def96hr = deformed96hrs_transferred + deformed96hrs_euthanized) %>%
   mutate(alive96hr = def96hr + final.tally) %>%
   group_by(spp, tempC, color, conclevel) %>%
   summarize(mean.perc.def = mean(def96hr/alive96hr), 
             se.perc.def = sd(def96hr/alive96hr)/n(), 
             nrep = n(), 
             nfish = sum(alive96hr) ) %>%
   data.frame()
   conc.sum2.def$se.perc.def[is.na(conc.sum2.def$se.perc.def)] <- 0
   add.nomconc2 = data.frame(conclevel = 0:5,
                         nomconc = c(0,10,100,500,1000,2000) )
   conc.sum2.def = merge(conc.sum2.def, add.nomconc2, all.x=T)

 # basic plot
 mean.def.plot2 = ggplot(data=conc.sum2.def, 
                         aes(x=log(nomconc+1), y=mean.perc.def, 
                             fill=factor(spp))) + 
   geom_errorbar(aes(ymin = mean.perc.def - se.perc.def, 
                     ymax = mean.perc.def + se.perc.def, 
                     width=0.75)) + 
   geom_point(pch=21, size=3) + 
   facet_grid(spp~tempC, scales="free", 
              labeller = labeller(tempC = c("12"="12C", "15"="15C", "18"="18C")) ) + 
   #scale_fill_manual(values=c("turquoise1","turquoise3","turquoise4"), guide="none") +
   scale_fill_manual(values=c("green3","grey80"), guide="none")+ 
   scale_x_continuous(name = "Nominal Pesticide Concentration",                                            breaks = log(c(0,10,100,1000,10000)+1),                                               labels=c(0,10,100,1000,10000) ) + 
   theme_bw() 
 
 # plot with y-scale from 0-50%
 mean.def.plot2 + scale_y_continuous(name = "Deformity Rate at 96hrs", 
                                       breaks = seq(0,.42,.1),
                                      # labels = seq(0,42,10), 
                                       limits=c(0,.42) )
 
tiff("figures/Deformities_WSGS_bytemp_forreport.jpeg",  width=600, height=300, units="px", compression="lzw", res=100)
  mean.def.plot2 + scale_y_continuous(name = "Deformity Rate at 96hrs", 
                                       breaks = seq(0,.42,.1), limits=c(0,.42))
dev.off()


## plot only controls to look at temp*spp effect
 mean.control.def.plot2 = ggplot(data=filter(conc.sum2.def, nomconc==0),
                         aes(x=tempC, y=mean.perc.def, 
                             fill=factor(spp))) + 
   geom_errorbar(aes(ymin = mean.perc.def - se.perc.def, 
                     ymax = mean.perc.def + se.perc.def)) + 
   geom_point(pch=21, size=3) + 
   facet_wrap(~spp, scales="free",
              labeller = labeller(spp = c("GS"="Green Sturgeon",
                                          "WS"="White Sturgeon")) ) + 
  # scale_fill_manual(values=c("turquoise1","turquoise3","turquoise4"), guide="none") +
   scale_fill_manual(values=c("green3","grey80"), guide="none")+ 
   scale_x_continuous(name = "Exposure Temperature (C)",                                            breaks = c(12,15,18))+ 
   scale_y_continuous(name = "Deformities at 96hrs (%)", 
        breaks = seq(0,.3, .05), labels=seq(0,30,5), limits=c(0,.3) ) +
   theme_bw() 
 
 
 
 # scaled to control plot
 cont.scales = filter(conc.sum2.def, nomconc==0)[,c(2,3,5)]
  names(cont.scales)[3] <- "cont.mean.perc.def"
 conc.sum2.def2 = merge(conc.sum2.def, cont.scales) 
 conc.sum2.def2$def.difference = conc.sum2.def2$mean.perc.def - conc.sum2.def2$cont.mean.perc.def
 
 mean.def.cont.plot2 = ggplot(data=conc.sum2.def2, 
                         aes(x=log(nomconc+1), y=def.difference, 
                             fill=factor(spp))) + 
   geom_errorbar(aes(ymin = def.difference - se.perc.def, 
                     ymax = def.difference + se.perc.def, 
                     width=.75)) + 
   geom_point(pch=21, size=3) + 
   facet_grid(spp~tempC, #scales="free", 
              labeller = labeller(tempC = c("12"="12C", "15"="15C", "18"="18C")) ) + 
   #scale_fill_manual(values=c("turquoise1","turquoise3","turquoise4"), guide="none") +
   scale_fill_manual(values=c("green3","grey80"), guide="none")+ 
   scale_x_continuous(name = "Nominal Pesticide Concentration",                                            breaks = log(c(0,10,100,1000,10000)+1),                                               labels=c(0,10,100,1000,10000) ) + 
  scale_y_continuous(name = "Standardized Deformity Rate at 96hrs", 
                                      breaks = seq(-0.1, .2,.05)) +
  geom_hline(yintercept=0, linetype="dashed", lwd=.2)+
   theme_bw() 
 
tiff("figures/DeformitiesStandardized_WSGS_bytemp_forreport.jpeg",  width=600, height=300, units="px", compression="lzw", res=100)
 mean.def.cont.plot2
dev.off() 
 
```

## stats for WS/GS by temp, bif (comp 2)
```{r stats for WS/GS comparing2 mort by temp, echo=FALSE}
chemanaly.bif = filter(chemanaly, contaminant=="bifenthrin", year %in% c(2022,2023))
#chemanaly.WS = filter(chemanaly.WS, !(contaminant %in% c("fipronil desulfinyl",
#                                                    "desulfinyl fipronil amide",
#                                                    "fipronil amide")))

conc.comp.bif <- mdat %>%
   filter(contaminant=="bifenthrin") %>%
   filter(year %in% c(2022,2023)) %>%
   data.frame()

conc.comp.bif2 = merge(conc.comp.bif, chemanaly.bif, all.X=T)
 conc.comp.bif2$calcconc <- as.numeric(conc.comp.bif2$calcconc)

conc.comp.bif2$logcalcconc = log(conc.comp.bif2$calcconc+1)                  


comp2.lm = lm(perc.mort ~ spp*logcalcconc*tempC, data=conc.comp.bif2)
plot(comp2.lm)
summary(comp2.lm)

# cbind is morts and survivors; all those deformed and euthanized on last day considerd survivors
comp2.glm.int = glm(cbind(total.exposure.morts, (total.accounted.for-total.exposure.morts)) ~ spp*logcalcconc + spp*tempC + logcalcconc*tempC, data=conc.comp.bif2, family="binomial",na.action=na.fail)
plot(comp2.glm.int ) # residuals look better here
summary(comp2.glm.int ) # nothing is significant 
dredge(comp2.glm.int ) # best model with only species, then spp+temp, then conc+spp (deltaAIC2.25). No support for interactions in model

comp2.glm.add = glm(cbind(total.exposure.morts, (total.accounted.for-total.exposure.morts)) ~ spp+logcalcconc+tempC, data=conc.comp.bif2, family="binomial",na.action=na.fail)
plot(comp2.glm.add ) # residuals look better here than the basic lm, same as glm.int
summary(comp2.glm.add ) # spp is now a significant variable
dredge(comp2.glm.add ) # AIC weights the same as glm.int (obviously)

# take home point: there is different mortality by species, but there is no effect of temperature or pesticide concentration (or thier interaction) on the mortality rates during the 96 hours of the trial.
```

```{r stats for WS/GS comparing2 deformity by temp, echo=FALSE}
chemanaly.bif = filter(chemanaly, contaminant=="bifenthrin", year %in% c(2022,2023))

conc.compdef.bif <- mdat %>%
   filter(contaminant=="bifenthrin") %>%
   filter(year %in% c(2022,2023)) %>%
   mutate(def96hr = deformed96hrs_transferred + deformed96hrs_euthanized) %>%
   mutate(alive96hr = def96hr + final.tally) %>%
   data.frame()

conc.compdef.bif2 = merge(conc.compdef.bif, chemanaly.bif, all.X=T)
 conc.compdef.bif2$calcconc <- as.numeric(conc.compdef.bif2$calcconc)

conc.compdef.bif2$logcalcconc = log(conc.compdef.bif2$calcconc+1)                  


compdef2.lm = lm(def96hr ~ spp*logcalcconc*tempC, data=conc.compdef.bif2)
plot(compdef2.lm)
summary(compdef2.lm)

# cbind is morts and survivors; all those deformed and euthanized on last day considerd survivors
compdef2.glm.int = glm(cbind(def96hr, (alive96hr-def96hr)) ~ spp*logcalcconc*tempC, data=conc.compdef.bif2, family="binomial",na.action=na.fail)
plot(compdef2.glm.int ) # residuals look better here, a few with strong leverage
summary(compdef2.glm.int ) # spp and temp significant variables
dredge(compdef2.glm.int ) # best model with temp and species and thier interaction, but adding concentration and conc*spp isn't too far behind (Delta AIC 1.55 with both, 1.83 with onlt conc)

compdef2.glm.partadd = glm(cbind(def96hr, (alive96hr-def96hr)) ~ spp*tempC + logcalcconc, data=conc.compdef.bif2, family="binomial",na.action=na.fail)
plot(compdef2.glm.partadd ) # fixes a few of the extreme residuals
summary(compdef2.glm.partadd ) # spp is only significant variable

```


## comparison 3 -> species specific responses, WS/GS at 15C, fip
```{r WS/GS comparing3 fip by spp, echo=FALSE}
conc.comp3 <- mdat %>%
   filter(tempC==15) %>%
   filter(contaminant=="fipronil") %>%
   data.frame()
   
 ggplot(data=conc.comp3, 
        aes(x=factor(nomconc), y=perc.mort, fill=contaminant)) + 
   geom_point(pch=21) + facet_grid(contaminant~spp)+#, scales="free") + 
   scale_fill_discrete(guide="none")+
     theme_bw()
 
## add measured concentrations before plotting
chemanaly.fip = filter(chemanaly, contaminant!="bifenthrin", sample=="spike")
  
  chemanaly.fip$log = log(as.numeric(chemanaly.fip$calcconc)+1)
   chemanaly.fip$calcconc <- NULL
  chemanaly.fipwide <- chemanaly.fip%>%  spread(key=contaminant, value=log)
    #fix column names
    names(chemanaly.fipwide)[5:10] <- paste0("log_",names(chemanaly.fipwide)[5:10])
    names(chemanaly.fipwide) <- str_replace_all(names(chemanaly.fipwide), " ", "_")


conc.comp.fip3 = merge(conc.comp3, chemanaly.fipwide, all.X=T)
  
 
 conc.sum3 <- conc.comp.fip3 %>%
   group_by(spp, tempC, contaminant, color, conclevel, nomconc, log_fipronil) %>%
   summarize(mean.perc.mort = mean(perc.mort), se.perc.mort = sd(perc.mort)/n(), nrep = n(),nfish = sum(total.accounted.for ) ) %>%
   data.frame()
 conc.sum3$se.perc.mort[is.na(conc.sum3$se.perc.mort)] <- 0


 mean.mort.plot3 = ggplot(data=conc.sum3, aes(x=log_fipronil, y=mean.perc.mort, fill=factor(spp))) + 
   geom_errorbar(aes(ymin = mean.perc.mort - se.perc.mort, 
                     ymax = mean.perc.mort + se.perc.mort,
                     width=.5)) + 
   geom_point(pch=21, size=2) + 
   facet_grid(spp~tempC, scales="free", labeller = labeller(tempC = c("15" = "15C")))+
   #             labeller = labeller(contaminant = c("bifenthrin" = "Bifenthrin, ng/L",
   #                                                "fipronil" = "Fipronil, ug/L"),
   #                                 spp = c("WS" = "White Sturgeon",
   #                                         "GS" = "Green Sturgeon")) ) + 
   scale_fill_manual(values=c("green3","grey80"), guide="none") + 
   scale_x_continuous(name = "Fipronil Concentration (ug/L)", breaks = log(c(0,1,10,100,1000)+1), labels=c(0,1,10,100,1000) ) + 
   theme_bw() 
 
 # mean.mort.plot3 + scale_y_continuous(name = "Mean Mortality", breaks = seq(0,.5,.1), labels=paste0(seq(0,50,10), "%"), limits=c(0,.5) )

 mean.mort.plot3 + scale_y_continuous(name = "Mean Mortality (%)", breaks = seq(0,.1,.02), labels=seq(0,10,2), limits = c(0,.1)) 

# tiff("figures/Mortality_GSWS_15C_forreport.jpeg",  width=600, height=300, units="px", compression="lzw", res=100)
#  mean.mort.plot3 + scale_y_continuous(name = "Mean Mortality (%)", breaks = seq(0,.1,.02), labels=seq(0,10,2), limits = c(0,.1)) 
# dev.off()
```

## stats for WS/GS at 15C, fip (comp 3)
```{r stats for WS/GS comparing3 fip by spp, echo=FALSE}
chemanaly.fip = filter(chemanaly, contaminant!="bifenthrin", sample=="spike")
#chemanaly.fip = filter(chemanaly.fip, !(contaminant %in% c("fipronil desulfinyl",
#                                                    "desulfinyl fipronil amide",
#                                                    "fipronil amide")))

chemanaly.fip$log = log(as.numeric(chemanaly.fip$calcconc)+1)
 chemanaly.fip$calcconc <- NULL
chemanaly.fipwide <- chemanaly.fip%>%  spread(key=contaminant, value=log)
#fix column names
names(chemanaly.fipwide)[5:10] <- paste0("log_",names(chemanaly.fipwide)[5:10])
names(chemanaly.fipwide) <- str_replace_all(names(chemanaly.fipwide), " ", "_")


conc.comp.fip <- mdat %>%
   filter(contaminant!="bifenthrin") %>%
   data.frame()

conc.comp.fip3 = merge(conc.comp.fip, chemanaly.fipwide, all.X=T)
 

comp3.lm1 = lm(perc.mort ~ spp + log_fipronil + log_fipronil_sulfide + log_fipronil_sulfone, data=conc.comp.fip3, na.action="na.fail")
plot(comp3.lm1)
summary(comp3.lm1)
car::vif(comp3.lm1) # very high VIF for the fip degredates (obviously)
 # fipronil sulfone has strongest effect size and smallest proportional se. Could use this, or could use fip because it's easier to describe

comp3.lm1a = lm(perc.mort ~ spp*log_fipronil, data=conc.comp.fip3, na.action="na.fail")
plot(comp3.lm1a)
summary(comp3.lm1a)

comp3.lm1b = lm(perc.mort ~ spp*log_fipronil_sulfone, data=conc.comp.fip3, na.action="na.fail")
plot(comp3.lm1b)
summary(comp3.lm1b)

# neither pesticide is significant, and the spp effect doesn't change. Use fip for ease of explanation

dredge(comp3.lm1a)
 # interaction not useful
 # best model is additive, without fip

comp3.lm2 = lm(perc.mort ~ spp + log_fipronil, data=conc.comp.fip3, na.action="na.fail")
plot(comp3.lm2)
summary(comp3.lm2)



comp3.glm = glm(cbind(total.exposure.morts, final.tally) ~ spp+ log_fipronil + log_fipronil_sulfide + log_fipronil_sulfone, data=conc.comp.fip3, family="binomial",na.action=na.fail)
plot(comp3.glm) # looks good
summary(comp3.glm) # spp is the largest / significant effect
dredge(comp3.glm) # model with oly spp is best, with 1.81AIC difference to model2 with pesticide concentration




## con't know where conc.sum3 came from upon revisiting code. re-wrote it...=/
 # mean.mort.plot3b = ggplot(data=conc.sum3, aes(x=log(calcconc+1), y=mean.perc.mort, fill=factor(spp), group=factor(spp)) ) + 
 #   geom_errorbar(aes(ymin = mean.perc.mort - se.perc.mort, 
 #                     ymax = mean.perc.mort + se.perc.mort),
 #                 width=.5) + 
 #   geom_point(pch=21, size=3) + 
 #   facet_grid(contaminant~spp, #scales="free", 
 #               labeller = labeller(contaminant = c("bifenthrin" = "Bifenthrin, ng/L",
 #                                                  "fipronil" = "Fipronil, ug/L")) ) + 
 #   scale_fill_manual(values=c("green4","grey80"), guide="none") + 
 #   scale_x_continuous(name = "Nominal Pesticide Concentration", breaks = log(c(0,10,100,1000,10000)+1), labels=c(0,10,100,1000,10000) ) + 
 #   theme_bw() 
 
 mean.mort.plot3b = ggplot(data=conc.comp.fip3, aes(x=log_fipronil, y=mean.perc.mort, fill=factor(spp), group=factor(spp)) ) + 
   geom_errorbar(aes(ymin = mean.perc.mort - se.perc.mort, 
                     ymax = mean.perc.mort + se.perc.mort),
                 width=.5) + 
   geom_point(pch=21, size=3) + 
   facet_grid(contaminant~spp, #scales="free", 
               labeller = labeller(contaminant = c("bifenthrin" = "Bifenthrin, ng/L",
                                                  "fipronil" = "Fipronil, ug/L")) ) + 
   scale_fill_manual(values=c("green4","grey80"), guide="none") + 
   scale_x_continuous(name = "Nominal Pesticide Concentration", breaks = log(c(0,10,100,1000,10000)+1), labels=c(0,10,100,1000,10000) ) + 
   theme_bw() 
 
 
mean.mort.plot3b + scale_y_continuous(name = "Mean Mortality (%)", breaks = seq(0,.1,.02), labels=seq(0,10,2), limits = c(0,.1)) 

tiff("figures/Mortality_GSWSfip_15C_forreport.jpeg",  width=400, height=400, units="px", compression="lzw", res=100)
mean.mort.plot3b + scale_y_continuous(name = "Mean Mortality (%)", breaks = seq(0,.1,.02), labels=seq(0,10,2), limits = c(0,.1))
dev.off()


# take home: there isn't a difference in mortality by concentration

```


## compiled plots
```{r patchwork plots for mortality and deformity, echo=FALSE}



tiff("figures/Mortality_GSWS_all_forreport.jpeg",  width=650, height=325, units="px", compression="lzw", res=100)

  (mean.mort.plot2 + scale_y_continuous(name = "Mean Mortality (%)", 
                                        breaks = seq(0,.1,.02), 
                                        labels=seq(0,10,2), limits = c(0,.1)) ) + 

   (mean.mort.plot3 + scale_y_continuous(name = "", 
                                        breaks = seq(0,.1,.02), 
                                        labels=seq(0,10,2), limits = c(0,.1)) )+ 

 plot_layout(ncol=2,  widths = c(3, 1)) + 
  
  plot_annotation(tag_levels = 'a')

dev.off()

```


## output tables from models
```{r stats tables for spp, pesticide, temp, conc}

# bifenthin
comp2.glm.add = glm(cbind(total.exposure.morts, (total.accounted.for-total.exposure.morts)) ~ spp+logcalcconc+tempC, data=conc.comp.bif2, family="binomial",na.action=na.fail)
summary(comp2.glm.add ) # spp is only significant variable

comp2.glm.add %>% tbl_regression(exponentiate=TRUE) %>%
  add_global_p()
  

#fipronil
comp3.glm = glm(cbind(total.exposure.morts, final.tally) ~ spp + log_fipronil + log_fipronil_sulfide + log_fipronil_sulfone, data=conc.comp.fip3, family="binomial",na.action=na.fail)

comp3.glm %>% tbl_regression(exponentiate=TRUE) %>%
  add_vif() %>%
  add_global_p()
  

      comp3.glm.fip = glm(cbind(total.exposure.morts, final.tally) ~ spp + 
                            log_fipronil, 
                          data=conc.comp.fip3, family="binomial",na.action=na.fail)
      
      comp3.glm.fip %>% tbl_regression(exponentiate=TRUE) %>%
        add_vif() %>%
        add_global_p()
      ## will use this, as the AIC and model fitting don't suggest any degredate is better than any other, and this is the parent compound so seems most reasonable to include. Can discuss the degredates in the paper but not the final report.  
      
      comp3.glm.fipsd = glm(cbind(total.exposure.morts, final.tally) ~ spp + 
                              log_fipronil_sulfide, 
                            data=conc.comp.fip3, family="binomial",na.action=na.fail)
      
      comp3.glm.fipsd %>% tbl_regression(exponentiate=TRUE) %>%
        add_vif() %>%
        add_global_p()
      
      comp3.glm.fipsn = glm(cbind(total.exposure.morts, final.tally) ~ spp + 
                              log_fipronil_sulfone, 
                            data=conc.comp.fip3, family="binomial",na.action=na.fail)
      
      comp3.glm.fipsn %>% tbl_regression(exponentiate=TRUE) %>%
        add_vif() %>%
        add_global_p()


      AIC(comp3.glm.fipsn, comp3.glm.fipsd, comp3.glm.fip) # i order, but very tiny differences)
      
      
# WS by bif and fip
comp.glm = glm(cbind(total.exposure.morts, final.tally) ~ contaminant*logcalcconc, data=conc.comp2, family="binomial", na.action=na.fail)
summary(comp.glm)

comp.glm %>% tbl_regression(exponentiate=TRUE) %>%
  add_global_p()


## deformities for bif by temp

compdef2.glm.partadd = glm(cbind(def96hr, (alive96hr-def96hr)) ~ spp*tempC + logcalcconc, data=conc.compdef.bif2, family="binomial",na.action=na.fail)
summary(compdef2.glm.partadd)

compdef2.glm.partadd %>% tbl_regression(exponentiate=TRUE) %>%
  add_global_p()
# significant interaction term, but likely because there is no deformities in WS the temperature effect can't exist for WS, so there has to be an interaction term


compdef2.glm.add = glm(cbind(def96hr, (alive96hr-def96hr)) ~ spp + tempC + logcalcconc, data=conc.compdef.bif2, family="binomial",na.action=na.fail)
summary(compdef2.glm.add)

compdef2.glm.add %>% tbl_regression(exponentiate=TRUE) %>%
  add_global_p()
# when we take out the interaction, there is a tiny probability of mortality for the WS (else it was an odd ratio very close to zero), amd the odds ratio for temperature is only slightly higher (0,75 vs 0..73 or so). 


```