---
title: "Exposure_Analysis2 - Exploratory Analysis"
author: "Anna Steel"
date: "9/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readtext) # need this because the ethovision output .txt files have unusual encoding as UTF-16
library(lme4)
library(circular)
#library(rethinking)
library(rprojroot) # only used for find_rstudio_root_file() to set project wd as root
library(rstatix)
library(viridis)
library(chron)

knitr::opts_knit$set(root.dir = find_rstudio_root_file()) # sets root directory to match project directory, not rmd file location
```

```{r utility functions, include=FALSE}
# calculate hypotenuse of triangle created by two xy locations

distmov = function(x1,x2,y1,y2) { dm = sqrt((x1-x2)^2 + (y1-y2)^2); return(dm)}

# calculate number steps between detections; use summarized dataset (5 pos/sec)
nstep = function(t2,t1, interv=0.2) {
  if (t2-t1 < 0) stop('time steps backwards?')
  nstep <- ( (t2-t1) / interv)
  return(nstep)
  }


circ.mean.na = function(x) {
  x2 = x[!is.na(x)]
  sinr <- sum(sin(x2))
  cosr <- sum(cos(x2))
  circmean <- atan2(sinr, cosr)
  return(circmean)
}

circ.disp.na = function(x) {
  x2 = x[!is.na(x)]
    n <- length(x2)
    c <- sum(cos(x2))
    s <- sum(sin(x2))
    r <- sqrt(c^2 + s^2)
    rbar <- r/n
    var <- 1 - rbar
    data.frame(n, r, rbar, var)
}

```


## Read in Cleaned Data ("Exposure_Analysis1_WSBIF2022.Rmd")
```{r read in clean data}
DataSum96temp.raw = read.csv("outputData/Exposure_Outputdata/Bifenthrin_2022_Cleaned_NoConc_96hrs.csv")
# DataSum2496.raw = read.csv("outputData/Exposure_Outputdata/Fipronil_2021_Cleaned_NoConc_2496hrs.csv")
 DataSumAll.raw = read.csv("outputData/Exposure_Outputdata/Bifenthrin_2022_Cleaned_Conc_Allhrs.csv")
```

```{r filter}
DataSum96temp <- DataSum96temp.raw[DataSum96temp.raw$tray!="C",]
```                   
## Add measured concentrations (versus nominal)
```{r chem analysis results}
# chemcsv.raw = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/ChemAnalysis_Fipronil_2021_Summary.csv")
#   chemcsv <- chemcsv.raw[chemcsv.raw$chemical=="fipronil" & chemcsv.raw$sample=="spike", c("spp", "nomconc", "calcConc")]
#  
#   
# DataSum96 <- merge(DataSum96.raw, chemcsv, by.x=c("Spp","Treatment"), by.y=c("spp","nomconc"), all.x=T)
#  DataSum96$calcConc = as.numeric(DataSum96$calcConc)
#  
 
```


## Add water temps at end of trial for 96 -->
```{r add indiv water temp increase}
# gstemp = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/Exposure_IndivBehaviorVideo_GS2021_Temps.csv")
# wstemp = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/Exposure_IndivBehaviorVideo_WS2021_Temps.csv")
# 
# # interpolate missing temps
# tempdat = rbind(gstemp, wstemp)
# tempdat$time <- times(paste0(tempdat$time, ":00"))
# 
# ggplot(data=tempdat, aes(x=time, y=endtemp)) + geom_point()
# 
# tempdat.redu = tempdat[!(tempdat$Exposure.Hr=="24" & tempdat$species=="WS" & tempdat$Tray %in% c("A","B","C","D")),] # legitimate notes for high temps for A,B, but also outliers for c,d if we're trying to make a high quality line for temp relationship with exposure video times
#  ggplot(data=tempdat.redu, aes(x=time, y=endtemp)) + geom_point(aes(color=species))
# 
# templm = lm(endtemp ~ time + species, data=tempdat.redu)
#  summary(templm) # temp = 6.83281 + 21.94528*time + 0.42187*WS + error
#  plot(templm)
# 
# tempdat$pred.endtemp[tempdat$species=="GS"] = 6.83281 + 21.94528*tempdat$time[tempdat$species=="GS"]
# 
# tempdat$pred.endtemp[tempdat$species=="WS"] = 6.83281 + 21.94528*tempdat$time[tempdat$species=="WS"] + 0.42187
# 
# ggplot(tempdat, aes(x=endtemp, y=pred.endtemp, color=species)) + geom_point() + geom_line(data = data.frame(x=14:20, y=14:20), aes(x=x, y=y), color="black", lty=2)
# 
# DataSum96.T = merge(DataSum96, tempdat, by.x=c("Spp","ExposureHrs","Tray","Replicate"), by.y=c("species","Exposure.Hr","Tray","rep"), all.x=T)
#  # this uses the control as a sample for all of the corresponding replicate numbers
# DataSum96 = DataSum96.T
```




## Exploratory Plots for each metric (Total distance travelled, Mean velocity, Meander and Turn angle, Use of center zone (% time), Time Active, Full Rotations vs distance traveled) 
  
  
### Distance  
  
```{r distance data, echo=F}

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum96$calcConc = DataSum96$nomconc_ngL ## temporary place holder until we get the results on conc back from Luann
DataSum96.dist = DataSum96 %>%
  group_by(Arena, rep, ExposureHrs, nomconc_ngL, tray, temp) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()

```

```{r distance boxplots}
## with 96
totfishdist96.bif22 = ggplot(DataSum96.dist, 
                             aes(fill=factor(nomconc_ngL), y=TotalfishDist_m, 
                               x=factor(nomconc_ngL) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~temp) + #, labeller = labeller(
                       # Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),#)+
                       # scales="free") +
                      ylab("Total Trial Distance (m)") + 
                      xlab("Nominal Bifenthrin Concentration (ng/L)") +
                      scale_fill_viridis_d(name="") + 
                      theme_bw()

totfishdist96.bif22


    
tiff("figures/Exposure_OutputFigs/TotalDistance_Bif_by_temp_raw.tiff", width=240, height=70, units="mm", compression="lzw", res=150)
totfishdist96.bif22
dev.off()


totfishdist96.biftemp22 = ggplot(DataSum96.dist, 
                             aes(fill=factor(nomconc_ngL), y=TotalfishDist_m, 
                               x=factor(temp) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(~nomconc_ngL) + #, labeller = labeller(
                       # Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),#)+
                       # scales="free") +
                      ylab("Total Trial Distance (m)") + 
                      xlab("Nominal Bifenthrin Concentration (ng/L)") +
                      scale_fill_viridis_d(name="") + 
                      theme_bw()

totfishdist96.biftemp22
```





### Sumarize time spent in center
```{r center zone data, echo=F} 
DataSum2496.centC = DataSum2496 %>%
  filter(!is.na(InZoneC)) %>%  ### will this bias the data if I remove those points where there isn't a detection? If the fish is more likely to be in the center when it's stationary, and it's more likely to be undetected when it's stationary, this may bias these values and under-represent the effect of the Fipronil (more stationary when strongly affected)
  # also note, this line doesn't actually change the results because summing the InZoneC column drops all NA automatically; this line above just makes that explicit
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T),# InZoneB = sum(InZoneB, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  #mutate(PercZoneC.2 = InZoneC / (InZoneC+InZoneB)) %>%
  # ran this comparison to see how much the NA can influence the data, and it seems to be minor
  ungroup()  %>%
  data.frame()


DataSumAll.centC = DataSumAll %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T), npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

```

```{r center zone plots, echo=F}

CenterC.plot = ggplot(DataSum2496.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
CenterC.plot


CenterCAll.plot = ggplot(DataSumAll.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
CenterCAll.plot

```

These are some pretty good plots for WS. I think I'll use the distance moved (most intuitive), the turn angle, and the centerC plots. 

```{r presentation plots}
totfishdist
sdMeander.plot
activefish
CenterC.plot
```


```{r final summarized datasets for opendata}

DataSumAll$SumTurnAngleAbs = abs(DataSumAll$SumTurnAngleRel)
DataSumAll$MeanderCircAbs = abs(DataSumAll$MeanderCirc)

DataSum.summarized = DataSum2496 %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(Spp, Contaminant, ExposureHrs, Treatment, calcConc, 
           Tray, Replicate, RepID) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100),
            MnVel = mean(MnVel, na.rm=T),
            MnTurnAngle = deg(circ.mean.na(rad(SumTurnAngleAbs))), 
            VarTurnAngle = deg(circ.disp.na(rad(SumTurnAngleAbs))$var), # circular variance
            MnMeander = mean(MeanderCircAbs, na.rm=T),
            SDMeander = sd(MeanderCircAbs, na.rm=T),
            CVMeander = sd(MeanderCircAbs, na.rm=T)/abs(mean(MeanderCircAbs, na.rm=T)),
            InZoneC = sum(InZoneC, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

write.csv(DataSum.summarized, "/Users/Anna/Documents/ResearchGit/SturgContam/outputData/Exposure_Outputdata/Bifenthrin_2020_Cleaned_Conc_Summarized.csv")


```