---
title: "Exposure_Analysis2 - Exploratory Analysis"
author: "Anna Steel"
date: "9/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readtext) # need this because the ethovision output .txt files have unusual encoding as UTF-16
library(lme4)
library(rethinking)
library(rprojroot) # only used for find_rstudio_root_file() to set project wd as root

knitr::opts_knit$set(root.dir = find_rstudio_root_file()) # sets root directory to match project directory, not rmd file location
```

```{r utility functions, include=FALSE}
# calculate hypotenuse of triangle created by two xy locations

distmov = function(x1,x2,y1,y2) { dm = sqrt((x1-x2)^2 + (y1-y2)^2); return(dm)}

# calculate number steps between detections; use summarized dataset (5 pos/sec)
nstep = function(t2,t1, interv=0.2) {
  if (t2-t1 < 0) stop('time steps backwards?')
  nstep <- ( (t2-t1) / interv)
  return(nstep)
  }


circ.mean.na = function(x) {
  x2 = x[!is.na(x)]
  sinr <- sum(sin(x2))
  cosr <- sum(cos(x2))
  circmean <- atan2(sinr, cosr)
  return(circmean)
}

circ.disp.na = function(x) {
  x2 = x[!is.na(x)]
    n <- length(x2)
    c <- sum(cos(x2))
    s <- sum(sin(x2))
    r <- sqrt(c^2 + s^2)
    rbar <- r/n
    var <- 1 - rbar
    data.frame(n, r, rbar, var)
}

```


## Read in Cleaned Data ("Exposure_Analysis1.Rmd")
```{r read in clean data}
DataSum2496 = read.csv("outputData/Exposure_Outputdata/Bifenthrin_2020_Cleaned_FullData.csv")
```


## Exploratory Plots for each metric (Total distance travelled, Mean velocity, Meander and Turn angle, Use of center zone (% time), Time Active, Full Rotations vs distance traveled) 
  
  
### Distance  
  
```{r distance data, echo=F}

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum2496.dist = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  ungroup()  %>%
  data.frame()
```

```{r distance plots}
totfishdist_hist = ggplot(DataSum2496.dist, aes(x=TotalfishDist_m) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(Treatment~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ #scales="free") +
                     theme_bw()

totfishdist = ggplot(DataSum2496.dist, aes(fill=factor(Treatment), y=TotalfishDist_m, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~Spp, labeller = labeller(
                        Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),#)+
                        scales="free") +
                      ylab("Total Trial Distance (m)") + 
                      xlab("Exposure Hours") +#("Bifenthrin Nominal Conc.") + 
                      scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()

totfishdist
```

```{r other ways of visualizing distance}

 # look at the CHANGE between mean distance of control (mean for treatment-exposurehrs) and target conc (each individual)
 
MeanDist0 = DataSum2496.dist %>%
  subset(Treatment==0) %>%
  group_by(Spp, ExposureHrs) %>%
  summarize(mean0_dist = mean(TotalfishDist_m)) %>%
  ungroup %>% data.frame
DataSumDiff.dist = merge(DataSum2496.dist, MeanDist0, all.x=T)
DataSumDiff.dist$DistDiff = DataSumDiff.dist$TotalfishDist_m - DataSumDiff.dist$mean0_dist


  cntrlfishdist = ggplot(DataSumDiff.dist, 
                         aes(y=DistDiff, x=factor(Treatment),fill=factor(Treatment) ) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                       geom_boxplot(outlier.size = .75) + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hours exposed","96"="96 hours exposed")))+
                       ylab("Change in Swimming Distance (m)\n treatment vs control") + 
                       xlab("Bifenthirin Nominal Conc") +
                       scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                       theme_bw()
                          
  cntrlfishdist

  
  
# look at the change between 24 and 96 hours for each replicated individual
 
DataSum2496.dist$ExposureHrsChr = paste0("ExpHr",DataSum2496.dist$ExposureHrs)
DataSum2496.dist$lnCalcConc = log(DataSum2496.dist$calcConc+1)

DataSumChg.dist = DataSum2496.dist %>%
  pivot_wider(id_cols = c(RepID, Treatment, Spp, Replicate, calcConc, lnCalcConc), 
              names_from = ExposureHrs, names_prefix="TotDistAt", 
              values_from = TotalfishDist_m) %>%
  mutate(chngdist = TotDistAt96 - TotDistAt24) %>%
  data.frame



  chngfishdist.box = ggplot(DataSumChg.dist, 
                           aes(y=chngdist/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Distance\nfrom 24 to 96 hrs of exposure (m)") + 
                    xlab("Bifenthirin Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                    theme_bw()
  
  chngfishdist.box
  
  
  chngfishdist.py = ggplot(DataSumChg.dist, 
                           aes(y=chngdist/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Distance\nfrom 24 to 96 hrs of exposure (m)") + 
                  xlab("log(Bifenthirin Concentration (ng/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishdist.py
  
  
# do individuals consistently respond in the same way? Should I add a multilevel term for intercept or slope. Or both?
  
ggplot(DataSum2496.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=RepID)) + geom_point() + geom_line() + facet_grid(Spp~Treatment, scales="free") + theme(legend.position="none")
# looks like there is often a trend, but not always. I think a random slope between the two time points would be really helpful. 

ggplot(DataSum2496.dist, aes(x=ExposureHrs, y=TotalfishDist_m, group=RepID, color=Spp)) + geom_point() + geom_line() + facet_grid(Treatment~Replicate, scales="free") + theme_bw() + theme(legend.position="none")

```

### modelling for distance is in ExposureAnalysis3.rmd





### Velocity 
```{r velocity data, echo=F}

## Summarize movement velocity
 
DataSum2496.vel = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  summarize(MnVel = mean(MnVel, na.rm=T), npos = n()) %>%
  ungroup()  %>%
  data.frame()
```

```{r velocity plots}

MoveVel.plot = ggplot(DataSum2496.vel, 
                           aes(fill=factor(Treatment), y=MnVel, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Mean movement velocity (mm/s)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

MoveVel.plot
```

```{r other ways of visualizing velocity}

 # look at the CHANGE between mean vel of control (mean for treatment-exposurehrs) and target conc (each individual)
 
MeanVel0 = DataSum2496.vel %>%
  subset(Treatment==0) %>%
  group_by(Spp, ExposureHrs) %>%
  summarize(mean0_Vel = mean(MnVel)) %>%
  ungroup %>% data.frame

DataSumDiff.Vel = merge(DataSum2496.vel, MeanVel0, all.x=T)

DataSumDiff.Vel$VelDiff = DataSumDiff.Vel$MnVel - DataSumDiff.Vel$mean0_Vel


  cntrlfishVel = ggplot(DataSumDiff.Vel, 
                         aes(y=VelDiff/10, x=factor(Treatment),fill=factor(Treatment) ) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                       geom_boxplot(outlier.size = .75) + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hours exposed","96"="96 hours exposed")))+
                       ylab("Change in Swimming Velocity\n treatment vs control") + 
                       xlab("Bifenthirin Nominal Conc") +
                       scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                       theme_bw()
                          
  cntrlfishVel

# look at the change between 24 and 96 hours for each treamtent-spp
 
DataSum2496.vel$ExposureHrsChr = paste0("ExpHr",DataSum2496.vel$ExposureHrs)

DataSumChg.Vel = DataSum2496.vel %>%
  select(-index, -Trial, -Arena,-ExposureHrs) %>%
  pivot_wider(names_from=ExposureHrsChr, values_from=MnVel) %>%
  mutate(chngVel = ExpHr96 - ExpHr24) %>%
  data.frame()


  chngfishVel.box = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure") + 
                    xlab("Bifenthirin Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                    theme_bw()
  
  chngfishVel.box
  
  
  chngfishVel.py = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure)") + 
                  xlab("log(Bifenthirin Concentration (ng/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishVel.py
  
```
# the trends look the same as distance, so for now I won't run models on velocity. Can add later if needed. 






### Meander and Turn Angle
```{r meander/turn angle data, echo=F}

## Summarize meander and turn angle
DataSum2496.meand = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(TurnAngleCirc))), 
            VarTurnAngle = deg(circ.disp.na(rad(TurnAngleCirc))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T))) %>%  
  ungroup()  %>%
  data.frame()


```

```{r meander/turn angle plots, echo=F}
meanMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()


mnTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

sdMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(SDMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Standard Deviation of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

CVMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(CVMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Coef-Var of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + ylim(c(0,100))+
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()


VarTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(VarTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Circular Variance of Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

meanMeander.plot
sdMeander.plot # this plot seems to show the cleanest trends and the tightest boxes. why?
CVMeander.plot
mnTurnangle.plot
VarTurnangle.plot
```
### modelling for meander is in ExposureAnalysis3.rmd






### Time moving (distance moved > .5mm)
```{r active time data, echo=F }

#WS need longer distance to see trend; mm=2 is good
#GS need shorter distance to see trend; mm=.5 is good
threshold_mm=.5

DataSum2496 <- mutate(DataSum2496,
                active = ifelse(SumDistMoved > threshold_mm, 1, 0))

PlotData_propactive = DataSum2496 %>%
  group_by(Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(npos=n(), nactive = sum(active), propactive = sum(active)/n() ) %>%
  ungroup() %>%
  data.frame()
```

```{r active time plots, echo=F}

activefish = ggplot(PlotData_propactive, 
                           aes(fill=factor(Treatment), y=propactive, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(
    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
    #scales="free") +
  ylab("proportion with active movement") + 
  xlab("Exposure Hours") +#("Bifenthrin Nominal Conc.") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()

activefish

```



## Sumarize time spent in center
```{r center zone data, echo=F} 
DataSum2496.centC = DataSum2496 %>%
  filter(!is.na(InZoneC)) %>%  ### will this bias the data if I remove those points where there isn't a detection? If the fish is more likely to be in the center when it's stationary, and it's more likely to be undetected when it's stationary, this may bias these values and under-represent the effect of the bifenthrin (more stationary when strongly affected)
  # also note, this line doesn't actually change the results because summing the InZoneC column drops all NA automatically; this line above just makes that explicit
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T), InZoneB = sum(InZoneB, na.rm=T), npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  mutate(PercZoneC.2 = InZoneC / (InZoneC+InZoneB)) %>%
  # ran this comparison to see how much the NA can influence the data, and it seems to be minor
  ungroup()  %>%
  data.frame()

```

```{r center zone plots, echo=F}

CenterC.plot = ggplot(DataSum2496.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Bifenthrin\nConcentration (ng/L)") + 
  theme_bw()
CenterC.plot

ggplot(DataSum2496.centC, aes(x=PercZoneC.1, y=PercZoneC.2)) + geom_point(pch=21) + geom_abline(a=0,b=1, color="steelblue3") + facet_wrap(~Spp) + theme_bw()
```

These are some pretty good plots for WS. I think I'll use the distance moved (most intuitive), the turn angle, and the centerC plots. 

```{r presentation plots}
totfishdist
meanMeander.plot
mnTurnangle.plot
activefish
CenterC.plot
```

