---
title: "Exposure_Analysis2 - Exploratory Analysis"
author: "Anna Steel"
date: "9/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readtext) # need this because the ethovision output .txt files have unusual encoding as UTF-16
library(lme4)
library(circular)
#library(rethinking)
library(rprojroot) # only used for find_rstudio_root_file() to set project wd as root
library(rstatix)
library(viridis)
library(chron)

knitr::opts_knit$set(root.dir = find_rstudio_root_file()) # sets root directory to match project directory, not rmd file location
```

```{r utility functions, include=FALSE}
# calculate hypotenuse of triangle created by two xy locations

distmov = function(x1,x2,y1,y2) { dm = sqrt((x1-x2)^2 + (y1-y2)^2); return(dm)}

# calculate number steps between detections; use summarized dataset (5 pos/sec)
nstep = function(t2,t1, interv=0.2) {
  if (t2-t1 < 0) stop('time steps backwards?')
  nstep <- ( (t2-t1) / interv)
  return(nstep)
  }


circ.mean.na = function(x) {
  x2 = x[!is.na(x)]
  sinr <- sum(sin(x2))
  cosr <- sum(cos(x2))
  circmean <- atan2(sinr, cosr)
  return(circmean)
}

circ.disp.na = function(x) {
  x2 = x[!is.na(x)]
    n <- length(x2)
    c <- sum(cos(x2))
    s <- sum(sin(x2))
    r <- sqrt(c^2 + s^2)
    rbar <- r/n
    var <- 1 - rbar
    data.frame(n, r, rbar, var)
}

```


## Read in Cleaned Data ("Exposure_Analysis1_BIF2022.Rmd")
```{r read in clean data}

DataSumAll.raw = read.csv("outputData/Exposure_Outputdata/Bifenthrin_2022_23_Cleaned_Conc_Allhrs.csv")

```

```{r filter}
# already missing WS-24hr-trayI (wrong video transfered), WS-96hr-trayC, GS-48hr-trayG, trayI, tray K (videos didn't record)

## Remove the 15 rows where the fish never moved at all; likely not tracking
# revisit after further ethovision review/edits 
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="A1" & tray=="B") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="B1" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="B3" & tray=="B") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="B3" & tray=="I") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="C2" & tray=="K") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="D1" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="D1" & tray=="I") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="D2" & tray=="K") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="C2" & tray=="L") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="C3" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==72 &
                  Arena=="A3" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==72 &
                  Arena=="B1" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==72 &
                  Arena=="C3" & tray=="L") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="C2" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="D3" & tray=="H") )





## Remove the 21 rows where the fish didn't move enough to get a single turn angle
# revisit after further ethovision review/edits 
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="A1" & tray=="I") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="A3" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="C1" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="C2" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="C3" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="D2" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="D3" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="D3" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="A1" & tray=="L") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="B1" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="B3" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="D2" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==72 &
                  Arena=="A2" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="A2" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="B1" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="B3" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="B3" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="C1" & tray=="C") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="C1" & tray=="D") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="D2" & tray=="H") )

DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==96 &
                  Arena=="D2" & tray=="I") )


## correct the mistaken nomconc assignments from trial list (correct tray orientation)
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="24" & DataSumAll.raw$spp=="WS" & 
                  DataSumAll.raw$tray%in% c("A","E") & 
                  DataSumAll.raw$Arena %in% c("B3","C2","D1"),]$nomconc_ngL <- 100

## correct nomconc for reversed trays (24hr, tray C,D; 96hr tray B,F)
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="24" & DataSumAll.raw$spp=="WS" & 
                  DataSumAll.raw$tray%in% c("C","D") & 
                  DataSumAll.raw$Arena %in% c("B3","C2","D1"),]$nomconc_ngL <- 0
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="24" & DataSumAll.raw$spp=="WS" & 
                   DataSumAll.raw$tray%in% c("C","D") & 
                   DataSumAll.raw$Arena %in% c("A2","B1","D3"),]$nomconc_ngL <- 10
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="24" & DataSumAll.raw$spp=="WS" & 
                  DataSumAll.raw$tray%in% c("C","D") & 
                  DataSumAll.raw$Arena %in% c("A3","B2","C1"),]$nomconc_ngL <- 100
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="24" & DataSumAll.raw$spp=="WS" & 
                  DataSumAll.raw$tray%in% c("C","D") & 
                  DataSumAll.raw$Arena %in% c("A1","C3","D2"),]$nomconc_ngL <- 500
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="96" & DataSumAll.raw$spp=="WS" & 
                   DataSumAll.raw$tray%in% c("B","F") & 
                   DataSumAll.raw$Arena %in% c("B3","C2","D1"),]$nomconc_ngL <- 0
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="96" & DataSumAll.raw$spp=="WS" & 
                   DataSumAll.raw$tray%in% c("B","F") & 
                   DataSumAll.raw$Arena %in% c("A2","B1","D3"),]$nomconc_ngL <- 10
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="96" & DataSumAll.raw$spp=="WS" & 
                  DataSumAll.raw$tray%in% c("B","F") & 
                  DataSumAll.raw$Arena %in% c("A3","B2","C1"),]$nomconc_ngL <- 100
DataSumAll.raw[DataSumAll.raw$ExposureHrs=="96" & DataSumAll.raw$spp=="WS" & 
                  DataSumAll.raw$tray%in% c("B","F") & 
                  DataSumAll.raw$Arena %in% c("A1","C3","D2"),]$nomconc_ngL <- 500

## remove two GS replicates where mean track meander is extremely small or large (no editing on tracks yet; revisit after manually edit tracks)
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="A1" & tray=="K") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==24 &
                  Arena=="B1" & tray=="J") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="WS" & ExposureHrs==24 &
                  Arena=="B2" & tray=="A") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="B1" & tray=="A") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="C2" & tray=="D") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==48 &
                  Arena=="D2" & tray=="C") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==72 &
                  Arena=="B1" & tray=="K") )
DataSumAll.raw = filter(DataSumAll.raw, !(spp=="GS" & ExposureHrs==72 &
                  Arena=="B3" & tray=="D") )

write.csv(DataSumAll.raw, "/Users/Anna/Documents/ResearchGit/SturgContam/outputData/Exposure_Outputdata/Bifenthrin_2022_23_Cleaned_Conc_FilteredPrelim_Alllhrs.csv")

```


```{r check sample size}
## Check remaining sample size
uniquereps  = unique(DataSumAll.raw[,c("spp","temp","ExposureHrs","tray","Arena","nomconc_ngL")])

table(uniquereps$ExposureHrs, uniquereps$temp, uniquereps$nomconc_ngL, 
      uniquereps$spp)
 # low reps for GS 18C @ 48hr (all nomconc) (5-6 per treatment)
```                   



## Add water temps at end of trial 
```{r add indiv water temp increase}
# gstemp = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/Exposure_IndivBehaviorVideo_GS2021_Temps.csv")
# wstemp = read.csv("//Users/Anna/Documents/ResearchGit/SturgContam/rawData/Exposure_IndivBehaviorVideo_WS2021_Temps.csv")
# 
# # interpolate missing temps
# tempdat = rbind(gstemp, wstemp)
# tempdat$time <- times(paste0(tempdat$time, ":00"))
# 
# ggplot(data=tempdat, aes(x=time, y=endtemp)) + geom_point()
# 
# tempdat.redu = tempdat[!(tempdat$Exposure.Hr=="24" & tempdat$species=="WS" & tempdat$Tray %in% c("A","B","C","D")),] # legitimate notes for high temps for A,B, but also outliers for c,d if we're trying to make a high quality line for temp relationship with exposure video times
#  ggplot(data=tempdat.redu, aes(x=time, y=endtemp)) + geom_point(aes(color=species))
# 
# templm = lm(endtemp ~ time + species, data=tempdat.redu)
#  summary(templm) # temp = 6.83281 + 21.94528*time + 0.42187*WS + error
#  plot(templm)
# 
# tempdat$pred.endtemp[tempdat$species=="GS"] = 6.83281 + 21.94528*tempdat$time[tempdat$species=="GS"]
# 
# tempdat$pred.endtemp[tempdat$species=="WS"] = 6.83281 + 21.94528*tempdat$time[tempdat$species=="WS"] + 0.42187
# 
# ggplot(tempdat, aes(x=endtemp, y=pred.endtemp, color=species)) + geom_point() + geom_line(data = data.frame(x=14:20, y=14:20), aes(x=x, y=y), color="black", lty=2)
# 
# DataSum96.T = merge(DataSum96, tempdat, by.x=c("Spp","ExposureHrs","Tray","Replicate"), by.y=c("species","Exposure.Hr","Tray","rep"), all.x=T)
#  # this uses the control as a sample for all of the corresponding replicate numbers
# DataSum96 = DataSum96.T
```




## Exploratory Plots for each metric (Total distance travelled, Mean velocity, Meander and Turn angle, Use of center zone (% time), Time Active, Full Rotations vs distance traveled) 
  
  
### Distance  
  
```{r distance data, echo=F}

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSumAll.dist = DataSumAll.raw %>%
  group_by(spp, ExposureHrs, Arena, tray, nomconc_ngL, temp) %>%
  #summarize(TotalfishDist = sum(SumDistMoved, na.rm=T)) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100)) %>%
  mutate(ExposureHrs = as.numeric(ExposureHrs)) %>%
  ungroup()  %>%
  data.frame()

# Use this to identify any fish with zero movement; consider erroneous tracking
check = DataSumAll.dist[DataSumAll.dist$TotalfishDist_m==0,]

```

```{r distance boxplots}

### with only 24hr and 96hr timepoints
DataSum2496.dist = filter(DataSumAll.dist, ExposureHrs %in% c(24, 96))

# totfishdist2496_hist = ggplot(DataSum2496.dist, aes(x=TotalfishDist_m) ) + 
#                      geom_histogram(bins=15) + 
#                      facet_wrap(nomconc_ngL~spp, labeller = labeller(
#                          spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
#                          #scales="free") +
#                      theme_bw()
# 
#     totfishdist2496_hist

totfishdist2496 = ggplot(DataSum2496.dist, 
                        aes(fill=factor(nomconc_ngL), y=TotalfishDist_m*100, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")) )+
                        #scales="free") +
                      ylab("Total Trial Distance (cm)") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    totfishdist2496


tiff("figures/Exposure_OutputFigs/TotalDistance_Bif_GSWS_2496hrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
totfishdist2496
dev.off()

 

### with all four timepoints
totfishdistAll_hist = ggplot(DataSumAll.dist, aes(x=TotalfishDist_m) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(nomconc_ngL~spp, labeller = labeller(
                         spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                         #scales="free") +
                     theme_bw()

    totfishdistAll_hist

totfishdistAll = ggplot(DataSumAll.dist, 
                        aes(fill=factor(nomconc_ngL), y=TotalfishDist_m*100, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Total Trial Distance (cm)") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    totfishdistAll


tiff("figures/Exposure_OutputFigs/TotalDistance_Bif_GSWS_allhrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
totfishdistAll
dev.off()

      
totfishdistAll_Control = ggplot(DataSumAll.dist[DataSumAll.dist$nomconc_ngL==0,], 
                                aes(y=TotalfishDist_m*100, 
                               x=factor((ExposureHrs+72)/24),
                               fill=spp) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C"))) +
                      ylab("Total Trial Distance (cm)") + 
                      xlab("Age (days post hatch)") +
                      scale_fill_manual(values=c("palegreen3","grey70"))+
                      theme_bw()
    
    totfishdistAll_Control
    
tiff("figures/Exposure_OutputFigs/TotalDistance_BifControl.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
totfishdistAll_Control
dev.off()
```





### Sumarize time spent in center
```{r center zone data, echo=F} 

DataSumAll.centC = DataSumAll.raw %>%
  filter(!is.na(InZone_C)) %>%  
  group_by(spp, ExposureHrs, Arena, tray, nomconc_ngL, temp) %>%
  summarize(InZoneC = sum(InZone_C, na.rm=T), npos = n()) %>%
  ungroup()  %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  data.frame()

DataSumAll.centB = DataSumAll.raw %>%
  filter(!is.na(InZone_B)) %>%  
  group_by(spp, ExposureHrs, Arena, tray, nomconc_ngL, temp) %>%
  summarize(InZoneB = sum(InZone_B, na.rm=T), npos = n()) %>%
  ungroup()  %>%
  mutate(PercZoneB.1 = InZoneB / npos) %>%
  data.frame()

```

```{r center zone plots, echo=F}
# only 2496hr
DataSum2496.centC <- filter(DataSumAll.centC, ExposureHrs%in%c(24,96))

CenterC2496.plot = ggplot(DataSum2496.centC, 
                           aes(fill=factor(nomconc_ngL), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
 # geom_violin()+
  facet_grid(spp~temp, 
             labeller = 
               labeller(spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C"))) +
  ylab("% of recorded positions in Central Zone C") + 
  xlab ("Exposure Hours") + 
   scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
   theme_bw()
CenterC2496.plot

tiff("figures/Exposure_OutputFigs/PercZone_BifTemp_GSWS_96hr.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
CenterC2496.plot
dev.off()

CenterCAll.plot = ggplot(DataSumAll.centC, 
                           aes(fill=factor(nomconc_ngL), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  geom_violin()+
  facet_grid(spp~temp, labeller = labeller(spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone C") + 
  xlab ("Exposure Hours") + 
  scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
    theme_bw()
CenterCAll.plot

tiff("figures/Exposure_OutputFigs/PercZone_BifTemp_GSWS_Allhr.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
CenterCAll.plot
dev.off()

# ZONE B INCLUDED MOST OF THE GS TRACKS; TOO WIDE OF A CENTER SPACE; STICK WITH ZONE C (15% OF TOTAL AREA)
# only 2496hr
DataSum2496.centB <- filter(DataSumAll.centB, ExposureHrs%in%c(24,96))

CenterB2496.plot = ggplot(DataSum2496.centB,
                           aes(fill=factor(nomconc_ngL), y=(PercZoneB.1),
                               x=factor(ExposureHrs) ) ) +
  geom_boxplot(outlier.size = .75) +
  facet_grid(spp~temp,
             labeller = labeller(spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone B") +
  xlab ("Exposure Hours") +
   scale_fill_manual(values=viridis(6)[1:4],
                              name="Nominal Bifenthrin\nConcentration (ng/L)") +
   theme_bw()

CenterB2496.plot
CenterC2496.plot

# 
# CenterBAll.plot = ggplot(DataSumAll.centB, 
#                            aes(fill=factor(nomconc_ngL), y=(PercZoneB.1), 
#                                x=factor(ExposureHrs) ) ) + 
#   geom_boxplot(outlier.size = .75) + 
#   #geom_violin()+
#   facet_grid(spp~temp, labeller = labeller(spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
#   ylab("% of recorded positions in Central Zone B") + 
#   xlab ("Exposure Hours") + 
#   scale_fill_manual(values=viridis(6)[1:4], 
#                               name="Nominal Bifenthrin\nConcentration (ng/L)") + 
#     theme_bw()
# CenterBAll.plot

```


### Turn Angle / Meander  
  
```{r summarize turn angles and meander, echo=F}

## Summarize to take total sum  of relative turn angles (-/+) for each fish 
DataSumAll.ta = DataSumAll.raw %>%
  group_by(spp, ExposureHrs, Arena, tray, nomconc_ngL, temp) %>%
  summarize(SumAbsTurnAngleRel_perFish = sum(abs(SumTurnAngleRel), na.rm=T),
            MnTurnAngleRel = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))) ) %>%
  ungroup()  %>%
  data.frame()

# Use this to identify any fish with problems
check = DataSumAll.ta[DataSumAll.ta$SumTurnAngleRel_perFish<90,]

## Summarize to take mean meander (relative turn angles/distance moved) for each fish 
DataSumAll.meand = DataSumAll.raw %>%
  group_by(spp, ExposureHrs, Arena, tray, nomconc_ngL, temp) %>%
  summarize(MnMeander = abs(mean(Meander, na.rm=T))) %>%
  ungroup()  %>%
  data.frame()

# Use this to identify any fish with problems
check2 = DataSumAll.meand[DataSumAll.meand$MnMeander<.0001,]
 check2 = check2[!is.na(check2$spp),]

```

```{r total turn angle boxplots}

### with only 24hr and 96hr timepoints
DataSumAll.ta$ExposureHrs = as.numeric(DataSumAll.ta$ExposureHrs )
DataSum2496.ta = filter(DataSumAll.ta, ExposureHrs %in% c(24,96))

DataSum2496.ta.hist = ggplot(DataSum2496.ta, aes(x=SumAbsTurnAngleRel_perFish) ) +
                     geom_histogram(bins=15) +
                     facet_wrap(nomconc_ngL~spp, labeller = labeller(
                         spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                         #scales="free") +
                     theme_bw()

    DataSum2496.ta.hist

TA2496 = ggplot(DataSum2496.ta, 
                        aes(fill=factor(nomconc_ngL), y=SumAbsTurnAngleRel_perFish, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Total Degrees Turned During Track") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    TA2496


tiff("figures/Exposure_OutputFigs/TurnAngle_Bif_GSWS_2496hrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
TA2496
dev.off()

 

### with all four timepoints

TA.All = ggplot(DataSumAll.ta, 
                        aes(fill=factor(nomconc_ngL), y=SumAbsTurnAngleRel_perFish, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Total Degrees Turned During Track") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    TA.All


tiff("figures/Exposure_OutputFigs/TurnAngle_Bif_GSWS_allhrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
TA.All
dev.off()

      
TA.All_Control = ggplot(DataSumAll.ta[DataSumAll.ta$nomconc_ngL==0,], 
                                aes(y=SumAbsTurnAngleRel_perFish, 
                               x=factor((ExposureHrs+72)/24),
                               fill=spp) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C"))) +
                      ylab("Total Degrees Turned During Track") + 
                      xlab("Age (days post hatch)") +
                      scale_fill_manual(values=c("palegreen3","grey70"))+
                      theme_bw()
    
    TA.All_Control
    
tiff("figures/Exposure_OutputFigs/TurnAngle_BifControl.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
TA.All_Control
dev.off()

```


```{r circular mean turn angle boxplots}

### with only 24hr and 96hr timepoints
DataSumAll.ta$ExposureHrs = as.numeric(DataSumAll.ta$ExposureHrs )
DataSum2496.ta = filter(DataSumAll.ta, ExposureHrs %in% c(24,96))

DataSum2496.ta.hist = ggplot(DataSum2496.ta, aes(x=MnTurnAngleRel) ) +
                     geom_histogram(bins=15) +
                     facet_wrap(nomconc_ngL~spp, labeller = labeller(
                         spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                         #scales="free") +
                     theme_bw()

    DataSum2496.ta.hist

TAc2496 = ggplot(DataSum2496.ta, 
                        aes(fill=factor(nomconc_ngL), y=MnTurnAngleRel, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Circular Mean of Absolute Turning Angle of Fish") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    TAc2496


tiff("figures/Exposure_OutputFigs/TurnAngle_CircMn_Bif_GSWS_2496hrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
TAc2496
dev.off()

 

### with all four timepoints

TAc.All = ggplot(DataSumAll.ta, 
                        aes(fill=factor(nomconc_ngL), y=MnTurnAngleRel, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Circular Mean of Absolute Turning Angle of Fish") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    TAc.All


tiff("figures/Exposure_OutputFigs/TurnAngle_CircMn_Bif_GSWS_allhrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
TAc.All
dev.off()

      
TAc.All_Control = ggplot(DataSumAll.ta[DataSumAll.ta$nomconc_ngL==0,], 
                                aes(y=MnTurnAngleRel, 
                               x=factor((ExposureHrs+72)/24),
                               fill=spp) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C"))) +
                      ylab("Circular Mean of Absolute Turning Angle of Fish") + 
                      xlab("Age (days post hatch)") +
                      scale_fill_manual(values=c("palegreen3","grey70"))+
                      theme_bw()
    
    TAc.All_Control
    
tiff("figures/Exposure_OutputFigs/TurnAngle_CircMn_BifControl.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
TA.All_Control
dev.off()

```


```{r meander boxplots}

### with only 24hr and 96hr timepoints
DataSumAll.meand$ExposureHrs = as.numeric(DataSumAll.meand$ExposureHrs )
DataSum2496.meand = filter(DataSumAll.meand, ExposureHrs %in% c(24,96))

Meand2496.hist = ggplot(DataSum2496.meand, aes(x=MnMeander) ) +
                     geom_histogram(bins=15) +
                     facet_wrap(nomconc_ngL~spp, labeller = labeller(
                         spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                         #scales="free") +
                     theme_bw()
Meand2496.hist
    

Meand2496 = ggplot(DataSum2496.meand, 
                        aes(fill=factor(nomconc_ngL), y=MnMeander*10, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Mean Track Meander (deg/cm)") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    Meand2496


tiff("figures/Exposure_OutputFigs/Meander_Bif_GSWS_2496hrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
Meand2496
dev.off()

 

### with all four timepoints
MeandAll = ggplot(DataSumAll.meand, 
                        aes(fill=factor(nomconc_ngL), y=MnMeander*10, 
                               x=factor(ExposureHrs) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C")),#)+
                        scales="free") +
                      ylab("Mean Track Meander (deg/cm)") + 
                      xlab("Exposure Hours") +
                      scale_fill_manual(values=viridis(6)[1:4], 
                              name="Nominal Bifenthrin\nConcentration (ng/L)") + 
                      theme_bw()
    
    MeandAll


tiff("figures/Exposure_OutputFigs/Meander_Bif_GSWS_allhrs.tiff", width=210, height=100, units="mm", compression="lzw", res=150)
MeandAll
dev.off()

      
MeanderAll_Control = ggplot(DataSumAll.meand[DataSumAll.meand$nomconc_ngL==0,], 
                                aes(y=MnMeander*10, 
                               x=factor((ExposureHrs+72)/24),
                               fill=spp) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_grid(spp~temp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                        temp = c("12"="12C", "15"="15C", "18"="18C"))) +
                      ylab("Mean Track Meander (deg/cm)") + 
                      xlab("Age (days post hatch)") +
                      scale_fill_manual(values=c("palegreen3","grey70"))+
                      theme_bw()
    
    MeanderAll_Control
    
tiff("figures/Exposure_OutputFigs/Meander_BifControl.tiff", width=140, height=70, units="mm", compression="lzw", res=150)
MeanderAll_Control
dev.off()

```




These are some pretty good plots for the report; sticking with 24 and 96hrs. 
```{r presentation plots}
totfishdist2496
CenterC2496.plot
Meand2496
TAc2496
```


```{r final summarized datasets for opendata}

DataSumAll.summarized = DataSumAll.raw %>%
  group_by(spp, ExposureHrs, nomconc_ngL, calcConc, tray, Arena, temp) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100),
            MnTurnAngle = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))), 
            VarTurnAngle = deg(circ.disp.na(rad(abs(SumTurnAngleRel)))$var),
            #MnTurnAngle = mean(abs(SumTurnAngleRel), na.rm=T),
            #VarTurnAngle = var(abs(SumTurnAngleRel), na.rm=T),
            MnMeander = mean(Meander, na.rm=T), 
            SDMeander = sd(Meander, na.rm=T),
            InZoneC = sum(InZone_C, na.rm=T), 
            npos = n())  %>%
  mutate(ExposureHrs = as.numeric(ExposureHrs), PropZoneC = InZoneC/npos) %>%
  ungroup()  %>%
  data.frame()

write.csv(DataSumAll.summarized, "/Users/Anna/Documents/ResearchGit/SturgContam/outputData/Exposure_Outputdata/Bifenthrin_2022_23_Cleaned_Conc_Summarized.csv")


```