---
title: "Exposure_Analysis2 - Exploratory Analysis"
author: "Anna Steel"
date: "9/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readtext) # need this because the ethovision output .txt files have unusual encoding as UTF-16
library(lme4)
library(circular)
library(rprojroot) # only used for find_rstudio_root_file() to set project wd as root
library(rstatix)
library(chron)

knitr::opts_knit$set(root.dir = find_rstudio_root_file()) # sets root directory to match project directory, not rmd file location
```

```{r utility functions, include=FALSE}
# calculate hypotenuse of triangle created by two xy locations

distmov = function(x1,x2,y1,y2) { dm = sqrt((x1-x2)^2 + (y1-y2)^2); return(dm)}

# calculate number steps between detections; use summarized dataset (5 pos/sec)
nstep = function(t2,t1, interv=0.2) {
  if (t2-t1 < 0) stop('time steps backwards?')
  nstep <- ( (t2-t1) / interv)
  return(nstep)
  }


circ.mean.na = function(x) {
  x2 = x[!is.na(x)]
  sinr <- sum(sin(x2))
  cosr <- sum(cos(x2))
  circmean <- atan2(sinr, cosr)
  return(circmean)
}

circ.disp.na = function(x) {
  x2 = x[!is.na(x)]
    n <- length(x2)
    c <- sum(cos(x2))
    s <- sum(sin(x2))
    r <- sqrt(c^2 + s^2)
    rbar <- r/n
    var <- 1 - rbar
    data.frame(n, r, rbar, var)
}

```


## Read in Cleaned Data ("Exposure_Analysis1.Rmd")
```{r read in clean data}

DataSumAll.raw = read.csv("outputData/Foraging_GSWS_Fipronil2021_Cleaned_Conc.csv")

DataSumAll.raw$exptTrialID = paste(DataSumAll.raw$spp, DataSumAll.raw$exptTrialID, DataSumAll.raw$barrel, sep="-")

DataSumAll.raw$Treatment = paste(DataSumAll.raw$spp, DataSumAll.raw$nomconc, DataSumAll.raw$prepost, sep="-")

DataSumAll.raw$TrialFullID = paste(DataSumAll.raw$exptTrialID, DataSumAll.raw$nomconc,  sep="-")
```


## remove erroneous top two concentrations and tidy data types
```{r remove top two conc}
DataSumAll.4 = filter(DataSumAll.raw, nomconc<=100)

DataSumAll.4$NotFound = as.numeric(substr(DataSumAll.4$SubjectNotFound, 1,3))

DataSumAll.4$TrialDateTime = as.POSIXct(DataSumAll.4$TrialDateTime, format="%m/%d/%Y %H:%M:%S", tz="Etc/GMT-8")

DataSumAll.4$prepost = factor(DataSumAll.4$prepost, level=c("Pre","Post"))

DataSumAll.4$TrackLength.sec = as.numeric(hms(substr(DataSumAll.4$TrackLength, 3, 14)))
```




## Exploratory Plots for each metric (Total distance travelled, Mean velocity, Meander and Turn angle, Use of zones (% time)) 
  
  
### Distance  
  
```{r distance data, echo=F}

## Summarize to take total distance (sum moved in a trial) for each fish replicate
DataSum.dist = DataSumAll.4 %>%
  group_by(exptTrialID, Treatment, TrialFullID,
           spp, nomconc, calcConc, prepost, barrel, 
           TrackLength.sec, NotFound, TrialDateTime,
           testtemp, tlmm, massg, hatchdate, dph,uniqueID) %>%
  summarise(TotalfishDist_cm = sum(SumDistMoved, na.rm=T)/(10),
            MnTurnAngle = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))), 
            VarTurnAngle = deg(circ.disp.na(rad(abs(SumTurnAngleRel)))$var), 
            MnMeander = mean(Meander, na.rm=T),
            SDMeander = sd(Meander, na.rm=T),
            InZoneAny = sum(InZone_Any, na.rm=T), npos = n()) %>% 
            # remember sometimes tidyverse is unabashedly British
  mutate(PercZoneAny = InZoneAny / npos) %>%
  ungroup()  %>%
  data.frame()
  
# checks
filter(as.data.frame(table(DataSum.dist$uniqueID)), Freq>2)

hist(DataSum.dist$NotFound)
 NotFound.filt = 20
 (nrow(filter(DataSum.dist, NotFound>NotFound.filt)) / nrow(DataSum.dist) )*100
   #if filter=25 then 5.2% of tracks removed
   #if filter=20 then 7.3% of tracks removed
   #if filter=15 then 10.9% of tracks removed
   #if filter=10 then 15.6% of tracks removed
 
 table(DataSum.dist$nomconc, DataSum.dist$prepost, DataSum.dist$spp)
 table(filter(DataSum.dist, NotFound<=NotFound.filt)$nomconc, 
       filter(DataSum.dist, NotFound<=NotFound.filt)$prepost, 
       filter(DataSum.dist, NotFound<=NotFound.filt)$spp)
 
DataSum.dist20 = filter(DataSum.dist, NotFound<=20) 
 
# standardize distance by track recording time
dist20.mean.length = mean(DataSum.dist20$TrackLength.sec)

DataSum.dist20$TotalfishDist_cmSTD = (DataSum.dist20$TotalfishDist_cm / DataSum.dist20$TrackLength.sec) * dist20.mean.length


#write.csv(DataSum.dist20, "outputData/Foraging_GSWS_Fip2021_Cleaned_Conc_Filtered_Dec2023.csv", row.names=F)

```

```{r distance boxplots}

totfishdist_hist = ggplot(DataSum.dist20, aes(x=TotalfishDist_cmSTD) ) + 
                     geom_histogram(bins=15) + 
                     facet_wrap(nomconc~spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+ #scales="free") +
                     theme_bw()

totfishdist = ggplot(DataSum.dist20, aes(x=factor(nomconc), y=TotalfishDist_cmSTD, 
                               fill=factor(prepost) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~spp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                        scales="free") +
                      ylab("Total Trial Distance (cm)\nStandardized by track duration") + 
                      xlab("Nominal Fipronil\nConcentration (ug/L)") +
                      scale_fill_discrete(name="Trial Period", 
                                          labels=c("Pre food cue","Post food cue")) + 
                      theme_bw()

totfishdist


totfishta = ggplot(DataSum.dist20, aes(x=factor(nomconc), y=MnTurnAngle, 
                               fill=factor(prepost) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~spp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                        scales="free") +
                      ylab("Mean Turn Angle (deg)") + 
                      xlab("Nominal Fipronil\nConcentration (ug/L)") +
                      scale_fill_discrete(name="Trial Period", 
                                          labels=c("Pre food cue","Post food cue")) + 
                      theme_bw()

totfishta + coord_cartesian(ylim=c(-15,15))



totfishmeand = ggplot(DataSum.dist20, aes(x=factor(nomconc), y=MnMeander, 
                               fill=factor(prepost) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~spp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                        scales="free") +
                      ylab("Mean point-to-point Meander (deg/mm)") + 
                      xlab("Nominal Fipronil\nConcentration (ug/L)") +
                      scale_fill_discrete(name="Trial Period", 
                                          labels=c("Pre food cue","Post food cue")) + 
                      theme_bw()

totfishmeand + coord_cartesian(ylim=c(-15,15))


totfishzone = ggplot(DataSum.dist20, aes(x=factor(nomconc), y=PercZoneAny, 
                               fill=factor(prepost) ) ) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~spp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                        scales="free") +
                      ylab("Percent of time near a feeding zone") + 
                      xlab("Nominal Fipronil\nConcentration (ug/L)") +
                      scale_fill_discrete(name="Trial Period", 
                                          labels=c("Pre food cue","Post food cue")) + 
                      theme_bw()

totfishzone
modz = glmer(cbind(InZoneAny, (npos-InZoneAny)) ~ I(log(calcConc))*prepost + (1|exptTrialID), data = DataSum.dist20, family="binomial")
summary(modz) #hm. maybe something interesting here


tiff("figures/Foraging_TotalDistanceSTD_nf20_Fip_GSWS.tiff", width=170, height=65, units="mm", compression="lzw", res=150)
totfishdist
dev.off()
```

```{r visualizing as dist change pre post}

 # look at the CHANGE between mean distance before and after, per fish


paired.trials = data.frame(table(DataSum.dist20$exptTrialID))
paired.trials = paired.trials[paired.trials$Freq>=2,"Var1"]

#DataSum.dist20 = DataSum.dist20[order(DataSum.dist20$exptTrialID, DataSum.dist20$prepost),]
# DataSum.distdiff = DataSum.dist20 %>%
#   filter(exptTrialID %in% paired.trials) %>%
#   mutate(mean.npos = mean(npos)) %>%
#   group_by(exptTrialID, spp, nomconc, barrel, calcConc, testtemp, tlmm, massg, TotalfishDist_cmSTD, npos) %>%
#   summarise(TotalDist_Diff = TotalfishDist_cmSTD[2] - TotalfishDist_cmSTD[1],
#             TotalDist_Diff_STDnpos = TotalDist_Diff*mean.npos) %>%
#   ungroup() %>% data.frame()
#   
  

DataSum.distdiff =filter(DataSum.dist20, prepost=="Pre", exptTrialID %in% paired.trials)
DataSum.distdiff$TotalDist_Diff = NA
DataSum.distdiff = DataSum.distdiff %>% rename(TotalfishDist_cmSTD_pre = TotalfishDist_cmSTD)

for(i in DataSum.distdiff$exptTrialID) {
    x = DataSum.dist20
    dif = x[x$exptTrialID == i & x$prepost=="Post","TotalfishDist_cmSTD"] - x[x$exptTrialID == i & x$prepost=="Pre","TotalfishDist_cmSTD"]
    DataSum.distdiff$TotalDist_Diff[DataSum.distdiff$exptTrialID==i] = dif
}
# value is how many more cm fish moved post than pre

hist(DataSum.distdiff$TotalDist_Diff)
hist(DataSum.distdiff$testtemp)



pre.post.diff = ggplot(data = DataSum.distdiff, aes(x=factor(nomconc), y=TotalDist_Diff, 
                       fill=spp)) + 
                      geom_boxplot(outlier.size = .75) + 
                      facet_wrap(~spp, labeller = labeller(
                        spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                        scales="free") +
                      ylab("Difference in Total Distance swam\nPre vs Post Food Addition")+ 
                              #(cm)\n(distances standardized by trial length)") + 
                      xlab("Nominal Fipronil Concentration (ug/L)") +
                      scale_fill_manual(values=c("green3","grey90"), guide=FALSE)+
                      theme_bw()

pre.post.diff

tiff("figures/Foraging_Diff_in_TotalDistanceSTD_nf20_Fip_GSWS.tiff", width=170, height=65, units="mm", compression="lzw", res=150)
pre.post.diff
dev.off()

```


## quick models for report
```{r quick foraging distance models}

GSdist = filter(DataSum.distdiff, spp=="GS")

m1.gs = lm(TotalDist_Diff ~ calcConc + testtemp + tlmm, data=GSdist)
 plot(m1.gs) # okay; some outliers at the top of the qqnorm
 summary(m1.gs) # no significant variables, when modeled as continuous
 
m2.gs = lm(TotalDist_Diff ~ factor(nomconc) + testtemp + tlmm, data=GSdist)
 plot(m2.gs) # okay; some outliers at the top of the qqnorm
 summary(m2.gs) # still no significant variables, when modeled with conc as factor
 anova(m2.gs)
  cC.emm <- emmeans(m2.gs, "nomconc")
  cC.emm; contrast(cC.emm, 'tukey') 

m3.gs = lm(TotalDist_Diff ~ calcConc + tlmm, data=GSdist)
 plot(m3.gs) # mostly the same as m1
 summary(m3.gs) # no significant variables, when modeled as continuous

m4.gs = lm(TotalDist_Diff ~ factor(calcConc), data=GSdist)
 plot(m4.gs) # mostly the same as m1
 anova(m4.gs)

 
 
WSdist = filter(DataSum.distdiff, spp=="WS")

m1.ws = lm(TotalDist_Diff ~ calcConc + testtemp + tlmm, data=WSdist)
 plot(m1.ws)# okay; some outliers at the top of the qqnorm but better than GS
 summary(m1.ws) # temperature significant, but not conc when continous predictor
 
m2.ws = lm(TotalDist_Diff ~ factor(nomconc) + testtemp + tlmm, data=WSdist)
 plot(m2.ws) # okay; some outliers at the top of the qqnorm but better than GS
 summary(m2.ws) # temp still only significant predictor; just too much variance to see diff
 anova(m2.ws)
  cC.emm <- emmeans(m2.ws, "nomconc")
  cC.emm; contrast(cC.emm, 'tukey') 

m3.ws = lm(TotalDist_Diff ~ calcConc + tlmm, data=WSdist)
 plot(m3.ws) # pretty good
 summary(m3.ws) # no significant variables, when modeled as continuous

m4.ws = lm(TotalDist_Diff ~ factor(calcConc), data=WSdist)
 plot(m4.ws) # pretty good
 anova(m4.ws) # still no significance

```

















#### copied from distance and not yet edited




### Velocity 
```{r velocity data, echo=F}

## Summarize movement velocity
 
DataSum2496.vel = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, calcConc, Spp, RepID) %>%
  summarize(MnVel = mean(MnVel, na.rm=T), npos = n()) %>%
  ungroup()  %>%
  data.frame()
```

```{r velocity plots}

MoveVel.plot = ggplot(DataSum2496.vel, 
                           aes(fill=factor(Treatment), y=MnVel, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")), scales="free") +
  ylab("Mean movement velocity (mm/s)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

MoveVel.plot
```

```{r other ways of visualizing velocity}

 # look at the CHANGE between mean vel of control (mean for treatment-exposurehrs) and target conc (each individual)
 
MeanVel0 = DataSum2496.vel %>%
  subset(Treatment==0) %>%
  group_by(Spp, ExposureHrs) %>%
  summarize(mean0_Vel = mean(MnVel)) %>%
  ungroup %>% data.frame

DataSumDiff.Vel = merge(DataSum2496.vel, MeanVel0, all.x=T)

DataSumDiff.Vel$VelDiff = DataSumDiff.Vel$MnVel - DataSumDiff.Vel$mean0_Vel


  cntrlfishVel = ggplot(DataSumDiff.Vel, 
                         aes(y=VelDiff/10, x=factor(Treatment),fill=factor(Treatment) ) ) + 
                       geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                       geom_boxplot(outlier.size = .75) + 
                       facet_grid(ExposureHrs~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"),
                         ExposureHrs = c("24"="24 hours exposed","96"="96 hours exposed")))+
                       ylab("Change in Swimming Velocity\n treatment vs control") + 
                       xlab("Fipronil Nominal Conc") +
                       scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                       theme_bw()
                          
  cntrlfishVel

# look at the change between 24 and 96 hours for each treamtent-spp
 
DataSum2496.vel$ExposureHrsChr = paste0("ExpHr",DataSum2496.vel$ExposureHrs)

DataSumChg.Vel = DataSum2496.vel %>%
  select(-index, -Trial, -Arena,-ExposureHrs) %>%
  pivot_wider(names_from=ExposureHrsChr, values_from=MnVel) %>%
  mutate(chngVel = ExpHr96 - ExpHr24) %>%
  data.frame()


  chngfishVel.box = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10,  x=factor(Treatment),fill=factor(Treatment) ) ) +
                   geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                   geom_boxplot(outlier.size = .75) + 
                    facet_wrap(~Spp, labeller = labeller(
                      Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                    ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure") + 
                    xlab("Fipronil Nominal Conc") +
                    scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
                    theme_bw()
  
  chngfishVel.box
  
  
  chngfishVel.py = ggplot(DataSumChg.Vel, 
                           aes(y=chngVel/10, x=log(calcConc+1), color=Spp ) ) + 
                  geom_hline(yintercept = 0, lwd=.6, linetype="dashed", color="red")+
                  geom_point() + 
                  facet_wrap(~Spp, labeller = labeller(
                    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
                  ylab("Change in Swimming Velocity\nfrom 24 to 96 hrs of exposure)") + 
                  xlab("log(Fipronil Concentration (ug/L))") +
                  scale_color_manual(values=c("green3","grey60")) + 
                  theme_bw()
  
  chngfishVel.py
  
```
# the trends look the same as distance, so for now I won't run models on velocity. Can add later if needed. 






### Meander and Turn Angle

```{r meander/turn angle data, echo=F}

## Summarize meander and turn angle
DataSum96.meand = DataSum96 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp) %>%#, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(TurnAngleCirc))), 
            VarTurnAngle = deg(circ.disp.na(rad(TurnAngleCirc))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSum96.mraw = DataSum96[!is.na(DataSum96$TurnAngle_deg),]


## Summarize meander and turn angle
DataSum2496.meand = DataSum2496 %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(TurnAngleCirc))), 
            VarTurnAngle = deg(circ.disp.na(rad(TurnAngleCirc))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSum2496.mraw = DataSum2496[!is.na(DataSum2496$TurnAngle_deg),]



## Summarize meander and turn angle
DataSumAll.meand = DataSumAll %>%
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, calcConc, RepID) %>%
  summarize(MnTurnAngle = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))), 
            VarTurnAngle = deg(circ.disp.na(rad(abs(SumTurnAngleRel)))$var), # circular variance
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)))  %>%
  ungroup()  %>%
  data.frame()

#keep raw data but remove missing points
DataSumAll.mraw = DataSumAll[!is.na(DataSumAll$TurnAngle_deg),]
```

```{r meander/turn angle plots 2496, echo=F}
meanMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
mnTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=abs(MnTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
sdMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(SDMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Standard Deviation of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

CVMeander.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(CVMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Coef-Var of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + ylim(c(0,100))+
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

VarTurnangle.plot = ggplot(DataSum2496.meand, 
                           aes(fill=factor(Treatment), y=(VarTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Circular Variance of Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()


meanMeander.plot
sdMeander.plot # this plot seems to show the cleanest trends and the tightest boxes. why?
CVMeander.plot
mnTurnangle.plot
VarTurnangle.plot
```

```{r meander/turn angle plots All, echo=F}
meanMeander.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=abs(MnMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
mnTurnangle.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=abs(MnTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Mean Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
  
sdMeander.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=(SDMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Standard Deviation of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

CVMeander.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=(CVMeander), 
                               x=factor(ExposureHrs) ) ) + geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Coef-Var of Meander (deg/mm)") + 
  xlab ("Exposure Hours") + ylim(c(0,100))+
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

VarTurnangle.plot = ggplot(DataSumAll.meand, 
                           aes(fill=factor(Treatment), y=(VarTurnAngle), 
                              x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("Circular Variance of Turn Angle (deg)") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()


meanMeander.plot
sdMeander.plot # this plot seems to show the cleanest trends and the tightest boxes. why?
CVMeander.plot
mnTurnangle.plot
VarTurnangle.plot
```

```{r visualizing as distns of percent change in circular turn angle at 96}
DataSum96.ta = DataSum96.meand

DataSum96.ta.cont = DataSum96.ta[DataSum96.ta$Treatment==0, c("Spp","ExposureHrs","Replicate","MnTurnAngle","VarTurnAngle")]
   DataSum96.ta.cont = rename(DataSum96.ta.cont,
                                 ControlMnTA = MnTurnAngle,
                                 ControlVarTA = VarTurnAngle)
   
DataSum96.ta.treat = DataSum96.ta[DataSum96.ta$Treatment!=0, c("Spp","ExposureHrs","Replicate","Treatment","MnTurnAngle","VarTurnAngle")]

DataSum96.ta.pseudowide = merge(DataSum96.ta.treat, DataSum96.ta.cont, all.x=T)

dist.func = function(a,b) { 
  g <- expand.grid(data.frame(a, b))
  PercDiff <- (g$b - g$a)/g$a
  return(PercDiff) 
  }
  
PercChg96 = DataSum96.ta.pseudowide %>%
  group_by(Spp, Treatment, Replicate) %>%
  summarize(PercChgMn_TA = dist.func(a=ControlMnTA, b=MnTurnAngle),
            PercChgVar_TA = dist.func(a=ControlVarTA, b=VarTurnAngle)) %>%
           ungroup() %>% data.frame()
PercChg96$Treatment = factor(PercChg96$Treatment)

  PercChgMnTA.GSlm = lm(PercChgMn_TA ~ Treatment, 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgMnTA.GSaov = aov(PercChgMnTA.GSlm)
    summary(PercChgMnTA.GSaov)
      emmeans(PercChgMnTA.GSlm, specs="Treatment") # dif from 0?
      TukeyHSD(PercChgMnTA.GSaov) # dif from eachother?
       # nothing is significantly different
     
    PercChgMnTA.WSlm = lm(PercChgMn_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgMnTA.WSaov = aov(PercChgMnTA.WSlm)
    summary(PercChgMnTA.WSaov)
      emmeans(PercChgMnTA.WSlm, specs="Treatment") # dif from 0?
      TukeyHSD(PercChgMnTA.WSaov)
       # nothing is significantly different
    
  PercChgVarTA.GSlm = lm(PercChgVar_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="GS",])
    PercChgVarTA.GSaov = aov(PercChgVarTA.GSlm)
    summary(PercChgVarTA.GSaov)
      TukeyHSD(PercChgVarTA.GSaov)
       # nothing is significantly different
     
    PercChgVarTA.WSlm = lm(PercChgVar_TA ~ factor(Treatment), 
                     data = PercChg96[PercChg96$Spp=="WS",])
    PercChgVarTA.WSaov = aov(PercChgVarTA.WSlm)
    summary(PercChgVarTA.WSaov)
      TukeyHSD(PercChgVarTA.WSaov)
       # nothing is significantly different from the other treatments
    
      
# are the boxes different from zero?      
onesamp.ttest <- PercChg96 %>%
  group_by(Spp, Treatment) %>%
  t_test(PercChgVar_TA~1) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance() %>%
  data.frame()
onesamp.ttest

      

DistnChgMnta.96= ggplot(PercChg96, 
                         aes(y=PercChgMn_TA, x=factor(Treatment),
                             fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, 
                                  linetype="dashed", color="black")+
                       geom_boxplot()+#outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                         scales="free" )+
                       geom_hline(yintercept = c(-0.5,0.5), lwd=.6, 
                              linetype="dashed", color="red") +
                       ylab("Change in Mean Turning Angle (deg)") + #ylim(c(-6,6)) +
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgMnta.96


DistnChgVarTA.96= ggplot(PercChg96, 
                         aes(y=PercChgVar_TA, x=factor(Treatment),
                             fill=factor(Treatment)) ) + 
                       geom_hline(yintercept = 0, lwd=.6, 
                                  linetype="dashed", color="black")+
                      geom_hline(yintercept = c(-0.5, 0.5), lwd=.3, 
                              linetype="dashed", color="red") +
                        geom_boxplot(outlier.shape=NA) +                      
  #geom_point(fill="grey60") + 
                       facet_grid(.~Spp, labeller = labeller(
                         Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")),
                         scales="free" )+
                       ylab("Change in Circular Variance \nof Turn Angle (deg)") + 
                        ylim(c(-1,1)) +
                       xlab("Fipronil Nominal Concentration") +
                       scale_fill_viridis_d(guide=F)+
                       theme_bw()
DistnChgVarTA.96


tiff("/Users/Anna/Documents/ResearchGit/SturgContam/figures/Exposure_OutputFigs/VarTA_Fip96_Perchg.tiff", width=142, height=70, units="mm", compression="lzw", res=150)
DistnChgVarTA.96
dev.off()

```


### modelling for meander is in ExposureAnalysis3.rmd






### Time moving (distance moved > .5mm)
```{r active time data, echo=F }

#WS need longer distance to see trend; mm=2 is good
#GS need shorter distance to see trend; mm=.5 is good
threshold_mm=.5

DataSum2496 <- mutate(DataSum2496,
                active = ifelse(SumDistMoved > threshold_mm, 1, 0))

PlotData_propactive = DataSum2496 %>%
  group_by(Replicate, ExposureHrs, Treatment, Spp, RepID) %>%
  summarize(npos=n(), nactive = sum(active), propactive = sum(active)/n() ) %>%
  ungroup() %>%
  data.frame()
```

```{r active time plots, echo=F}

activefish = ggplot(PlotData_propactive, 
                           aes(fill=factor(Treatment), y=propactive, 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  facet_wrap(~Spp, labeller = labeller(
    Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon")))+
    #scales="free") +
  ylab("proportion with active movement") + 
  xlab("Exposure Hours") +#("Fipronil Nominal Conc.") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()

activefish

```





### Sumarize time spent in center
```{r center zone data, echo=F} 
DataSum2496.centC = DataSumAll.raw %>%
  filter(ExposureHrs %in% c(24,96)) %>%
  filter(!is.na(InZoneC)) %>%  ### will this bias the data if I remove those points where there isn't a detection? If the fish is more likely to be in the center when it's stationary, and it's more likely to be undetected when it's stationary, this may bias these values and under-represent the effect of the Fipronil (more stationary when strongly affected)
  # also note, this line doesn't actually change the results because summing the InZoneC column drops all NA automatically; this line above just makes that explicit
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID, Tray) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T),# InZoneB = sum(InZoneB, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  #mutate(PercZoneC.2 = InZoneC / (InZoneC+InZoneB)) %>%
  # ran this comparison to see how much the NA can influence the data, and it seems to be minor
  ungroup()  %>%
  data.frame()


DataSumAll.centC = DataSumAll.raw %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(index, Trial, Arena, Replicate, ExposureHrs, Treatment, Spp, RepID, Tray) %>%
  summarize(InZoneC = sum(InZoneC, na.rm=T), npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

```

```{r center zone plots, echo=F}

CenterC.plot2496 = ggplot(DataSum2496.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions\nin Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
CenterC.plot2496


tiff("figures/Exposure_OutputFigs/PercZone_Fip_GSWS_2496hr.tiff", width=170, height=65, units="mm", compression="lzw", res=150)
CenterC.plot2496
dev.off()




CenterCAll.plot = ggplot(DataSumAll.centC, 
                           aes(fill=factor(Treatment), y=(PercZoneC.1), 
                               x=factor(ExposureHrs) ) ) + 
  geom_boxplot(outlier.size = .75) + 
  #geom_violin()+
  facet_wrap(~Spp, labeller = labeller(Spp = c("GS"="Green Sturgeon","WS"="White Sturgeon"))) +
  ylab("% of recorded positions in Central Zone") + 
  xlab ("Exposure Hours") + 
  scale_fill_viridis_d(name="Nominal Fipronil\nConcentration (ug/L)") + 
  theme_bw()
CenterCAll.plot

tiff("figures/Exposure_OutputFigs/PercZone_Fip_GSWS_Allhrs.tiff", width=140, height=45, units="mm", compression="lzw", res=150)
CenterCAll.plot
dev.off()



```

These are some pretty good plots for WS. I think I'll use the distance moved (most intuitive), the turn angle, and the centerC plots. 

```{r presentation plots}
totfishdist
sdMeander.plot
activefish
CenterC.plot
```

```{r final summarized datasets for opendata}

DataSumAll.summarized = DataSumAll.T %>%
  filter(!is.na(InZoneC)) %>%  
  group_by(Spp, Contaminant, ExposureHrs, Treatment, calcConc, 
           Tray, Replicate, index, RepID, endtemp, pred.endtemp) %>%
  summarize(TotalfishDist_m = sum(SumDistMoved, na.rm=T)/(10*100),
            MnVel = mean(MnVel, na.rm=T),
            MnTurnAngle = deg(circ.mean.na(rad(abs(SumTurnAngleRel)))), 
            VarTurnAngle = deg(circ.disp.na(rad(abs(SumTurnAngleRel)))$var), # circ. var.
            MnMeander = mean(MeanderCirc, na.rm=T),
            SDMeander = sd(MeanderCirc, na.rm=T),
            CVMeander = sd(MeanderCirc, na.rm=T)/abs(mean(MeanderCirc, na.rm=T)),
            InZoneC = sum(InZoneC, na.rm=T), 
            npos = n()) %>%
  mutate(PercZoneC.1 = InZoneC / npos) %>%
  ungroup()  %>%
  data.frame()

write.csv(DataSumAll.summarized, "/Users/Anna/Documents/ResearchGit/SturgContam/outputData/Exposure_Outputdata/Fipronil_2021_Cleaned_Conc_Summarized.csv")


```